---
title: "00_DemoVignette"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(here)
library(tidyverse)
library(janitor)

library(zoo)
library(readABF)

library(broom)
library(minpack.lm) # getting Tau
library(patchwork)
library(ggsci)
library(cowplot)
library(patchwork)


library(minpack.lm) # for use in fit_tau_1term_exp()

theme_set(ggplot2::theme_minimal())

library(devtools)
devtools::load_all()
```

```{r}
abf_dir_path <- "D:/0000_Traces_mRNA24hLC/"
```



## Handling different kinds of files (Proof of principle)
###Load in data (ionic currents)
```{r}
file_list <- list(FI = "190903_0025.abf",
                  EPSP = "190903_0023.abf",
                  GJCC = "190903_0021.abf", 
                  GJVC = "190903_0020.abf",
                  
                  HTK  = "190903_0031.abf",
                  HTKC = "190903_0034.abf",
                  A    = "190903_0030.abf",
                  AC   = "190903_0033.abf")

trace_list <- map(seq_along(file_list), function(i){
  temp <- readABF_as_matrix2(path = paste0(abf_dir_path, 
                                           # "C:/Users/Daniel/Documents/Trace_Holding/", 
                                           file_list[[i]]),
                     channels = "all",
                     relative.time = T) %>%
    as.data.frame() %>% 
    janitor::clean_names(case = "upper_camel") %>% 
    mutate(Sweep = as.factor(Sweep)) %>% 
    group_by(Sweep) %>% 
    mutate(MinTime = min(Time, na.rm = T)) %>% 
    mutate(Time = Time - MinTime) %>% 
    select(-MinTime)
})

names(trace_list) <- names(file_list)
```

### Show all
```{r}
example_plots <- map(trace_list, function(i){
  downsample_data(i, len = 5000) %>%
    ungroup() %>% 
    gather(Ch, Value, c("In4","In7","In9","In12")) %>% 
    mutate(Cell = case_when(Ch %in% c("In4","In7") ~ "Cell A",
                            Ch %in% c("In9","In12") ~ "Cell B",)) %>% 
    mutate(ChType = case_when(Ch %in% c("In4","In9") ~ "mV",
                              Ch %in% c("In7","In12") ~ "nA",)) %>% 
    mutate(Ch = factor(.$Ch, levels = c("In4","In7","In9","In12"))) %>% 
    ggplot(aes(Time, Value, group = Sweep, color = Cell))+
    geom_line()+
    facet_wrap(ChType~Cell, scales = "free_y", ncol = 2)+
    labs(y = "")+
    theme(legend.position = "")+
    scale_color_aaas()
})

plot_grid(plotlist = example_plots)
```


###GJVC
```{r}
## GJVC: get Ig, Ileak====
temp <- trace_list$GJVC
### Setup



i_leak <- temp %>%
  filter(Time > 0.75) %>%
  mutate(In4 = as.numeric(In4)) %>%
  mutate(In7 = as.numeric(In7))

i_leak <- i_leak %>% 
  mutate(Segment = ifelse(Time >= 0.8 & Time <= 1.0, "PreStep", 
                          ifelse(Time >= 1.2 & Time <= 1.25, "Step", 
                                 "NA" ))) %>% 
  group_by(Sweep, Segment) %>% 
  mutate(In4Mean = mean(In4, na.rm = T),
         In7Mean = mean(In7, na.rm = T),
         In9Mean = mean(In9, na.rm = T),
         In12Mean = mean(In12, na.rm = T))

### Ig 
downsample_data(i_leak, len = 1000) %>% 
  gather("key", "value", c("In4", "In9")) %>% 
  ggplot(aes(Time, value, color = Segment, group = Sweep))+
  geom_path()+
  facet_grid(.~key)

i_g <- i_leak %>% 
  select(Sweep, Segment, In4Mean, 
         #In7Mean, 
         # In9Mean, 
         In12Mean
         ) %>% 
  filter(Segment != "NA") %>% 
  distinct() %>% 
  pivot_wider(names_from = "Segment", 
              values_from = c("In4Mean", "In12Mean")) %>% 
  mutate(In4Mean_Step = In4Mean_Step - In4Mean_PreStep,
         In12Mean_Step = In12Mean_Step - In12Mean_PreStep) %>% 
  select(Sweep, In4Mean_Step, In12Mean_Step) %>%
  rename(In4Mean = In4Mean_Step, In12Mean = In12Mean_Step) %>% 
  filter(abs(In4Mean) >= 4) 

i_g %>% 
  ggplot(aes(In4Mean, In12Mean))+
  geom_smooth(method = lm)+
  geom_point()

In4_to_In9_Ig <- as.numeric(broom::tidy(lm(In12Mean ~ In4Mean, data = i_g))[2, "estimate"])


### Ileak
i_leak %>% 
  ggplot(aes(Time, In4, color = Segment, group = Sweep))+
  geom_path()

i_leak <- i_leak %>% 
  ungroup() %>%
  select(Sweep, Segment, In4Mean, In7Mean) %>% 
  filter(Segment != "NA") %>% 
  distinct() %>% 
  filter(abs(In4Mean + 60) > 3 )
  
fm <- lm(In4Mean ~ In7Mean, data = i_leak)

In4_R <- as.numeric(broom::tidy(fm)[2, "estimate"])
```

###GJCC
```{r}
## GJCC: get CC, R_C, C, Rin ====
temp <- trace_list$GJCC

temp_plt <- temp %>% 
  filter(Sweep == 4) %>%
  mutate(In4 = as.numeric(In4)) %>% 
  mutate(In7 = as.numeric(In7))

# Show what the protocol looks like
plt1 <- downsample_data(temp_plt, len = 1000) %>% 
  gather(key, value, c("In4", "In9")) %>% 
  ggplot(aes(Time, value, color = key))+
  geom_path()

plt2 <- downsample_data(temp_plt, len = 1000) %>% 
  gather(key, value, c("In7", "In12")) %>% 
  mutate(key = factor(.$key, levels = c("In7", "In12"))) %>% 
  ggplot(aes(Time, value, color = key))+
  geom_path()

plt1/plt2

# annotate
temp <- temp %>% 
   mutate(Segment = case_when(Time >= 0       & Time <= 0.32820 ~ "A", #"PreStepIn12",
                              Time >= 1.32836 & Time <= 1.82836 ~ "B", #"StepIn12",
                              Time >= 2.57744 & Time <= 3.07744 ~ "C", #"PreStepIn7",
                              Time >= 4.07760 & Time <= 4.57760 ~ "D", #"StepIn7"
                              ))
```
$$r_{11}=\frac{v_1}{i_1}$$
$$r_{12}=\frac{v_2}{i_1}$$
$$r_1= \frac{r_{11}*r_{22} - r_{12}^2}{r_{22} - r_{12}}$$
$$r_c = \frac{r_{11}*r_{22} - r_{12}^2}{r_{12}}$$
```{r}
temp_resist <- temp %>% 
  group_by(Sweep, Segment) %>% 
  filter(!is.na(Segment)) %>% 
  summarise(MeanIn4 = mean(In4, na.rm = T),
            MeanIn7 = mean(In7, na.rm = T),
            MeanIn9 = mean(In9, na.rm = T),
            MeanIn12 = mean(In12, na.rm = T)) %>% 
  pivot_wider(names_from = Segment, values_from = c("MeanIn4", "MeanIn7", "MeanIn9", "MeanIn12")) %>% 
  mutate(In4_CC = MeanIn9_D/MeanIn4_D, #inj in In4
         In4_R11 = MeanIn4_D/MeanIn7_D,
         In4_R12 = MeanIn9_D/MeanIn7_D,

         
         In9_CC = MeanIn4_B/MeanIn9_B, #inj in In9
         In9_R11 = MeanIn9_B/MeanIn12_B,
         In9_R12 = MeanIn4_B/MeanIn12_B
         ) %>% 
  mutate(mean_R12 = (In4_R12+In9_R12)/2) %>% 
  mutate(In4_R1 = ((In4_R11*In9_R11) - (mean_R12^2)) / (In9_R11-mean_R12),
         In4_Rc = ((In4_R11*In9_R11) - (mean_R12^2)) / (mean_R12),
         
         In9_R1 = ((In9_R11*In4_R11) - (mean_R12^2)) / (In4_R11-mean_R12),
         In9_Rc = ((In9_R11*In4_R11) - (mean_R12^2)) / (mean_R12)
         ) %>% select(starts_with("In"))
```

```{r}
# V_rest
temp_rmp <- temp %>% 
  filter(Segment == "C") %>% 
  group_by(Sweep) %>% 
  summarise(In4_Vrest = min(In4, na.rm = T),
            In9_Vrest = min(In9, na.rm = T))
```


```{r}
# Tau
temp <- temp %>% 
   mutate(Segment = case_when(Time >= 3.07744 & Time <= 4.57760 ~ "In4Step", #"PreStepIn7",
                              Time >= 0.32820 & Time <= 1.82836 ~ "In9Step", #"StepIn7"
                              ))  

plt1 <- 
  downsample_data(temp, len = 1000) %>% 
  gather(Key, Value, c("In4", "In9")) %>% 
  ggplot(aes(Time, Value, color = Segment, group = interaction(Key, Sweep)))+
  geom_path()

plt2 <- 
  downsample_data(temp, len = 1000) %>% 
  ungroup() %>% 
  gather(key, value, c("In7", "In12")) %>% 
  mutate(key = factor(.$key, levels = c("In7", "In12"))) %>% 
  ggplot(aes(Time, value, color = Segment, group = interaction(key, Sweep)))+
  geom_path()

plt1/plt2

### test minpack.lm ####
# install.packages("minpack.lm")


temp_in9 <- temp %>% 
  filter(Segment == "In9Step") %>% 
  mutate(Time = Time - min(Time, na.rm = T))

test_fits <- map(unique(temp_in9$Sweep), function(i){
  fit_tau_1term_exp(df = filter(temp_in9, Sweep == i),
                    IV = "Time",
                    DV = "In9")  
})

test_fits_plts <- map(seq_along(test_fits), function(i){
  ggplot()+
    geom_line(data = as.data.frame(test_fits[[i]]$check_fit), aes(x = Time, y = Fit), color = "firebrick")+
    geom_line(data = as.data.frame(test_fits[[i]]$check_fit), aes(x = Time, y = In9), alpha = 0.8)+
    labs(subtitle = paste("tau =", as.character(
      round(test_fits[[i]]$fit[2, 2], digits = 3)
      )))
})

cowplot::plot_grid(plotlist = test_fits_plts)
```

###FI
```{r}
temp <- trace_list$FI

downsample_data(df = temp, len = 5000) %>% 
  gather(key, value, c("In9", "In12")) %>% 
  ungroup() %>% 
  mutate(key = factor(.$key, levels = c("In9", "In12"))) %>% 
  ggplot(aes(Time, value, group = Sweep))+
  geom_line()+
  facet_wrap(key~., scales = "free_y", ncol = 1)

#r11 == ~15.3
#r1 == ~17.9

place_params_for_predict_voltage_trace(tau = 19.9, 
                                       Rin = 15.3)

# place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == 10, ], 
#                                      Time.ch = "Time", 
#                                      Inj.ch = "In12")
# 
# run_predict_voltage_trace_py()
# 
# predicted_response <- retrieve_predicted_voltage()

predicted_response_list <- map(1:11, function(i){
  place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == i, ], 
                                       Time.ch = "Time", 
                                       Inj.ch = "In12")
  
  run_predict_voltage_trace_py()
  
  predicted_response <- retrieve_predicted_voltage()
  return(predicted_response)
})


my_plts <- map(
  seq_along(predicted_response_list),
  function(i){
    ggplot()+
      geom_line(data = predicted_response_list[[i]], aes(Time, predicted-56.5))+
      geom_line(data = temp[temp$Sweep == i, ], aes(Time, In9), color = "red")+
      labs(x = "Seconds", y = "mV")+
      coord_cartesian(y = c(-150, +120))
  })

# cowplot::plot_grid(plotlist = my_plts)


my_plts[[11]] / my_plts[[11 - 2]] / my_plts[[1 + 2]] / my_plts[[1]]
```

###EPSP
(epsp) How could we slice up the trace? 
```{r}
## Here's the stimulus used in the protocol ====
# sweep duration should be 19.687 seconds
epsp_stim <- readABF_as_matrix(here("inst", "extdata", "epsp_stim_files", "08 current injection.abf"),
                  channels = "Axo1I2")
epsp_stim <- as_tibble(epsp_stim) %>%
  mutate(Time = Time - min(Time, na.rm = T)) %>%
  rename(Stim = Axo1I2)


shading_annotations <- data.frame(
  starts = c(0.40,
             4.87,
             10.74,
             16.74),
  next_start = c(4.87,
                 10.74,
                 16.74,
                 19.685),
  equal_len = c(0.40,
                4.87,
                10.74,
                16.74) + 2.945,
  on_end = c(2,
             6.17,
             12.54, 
             18.5),
  equal_on = c(0.40,
               4.87,
               10.74,
               16.74) + 1.30
)

ggplot()+
  geom_vline(xintercept = c(shading_annotations$starts, shading_annotations$equal_len, shading_annotations$next_start, shading_annotations$equal_on), color = "gray")+
    geom_path(data = epsp_stim, aes(Time, Stim+1.5))+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = next_start, ymin = 0, ymax = 0.5), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[1], color = RColorBrewer::brewer.pal(3, "Set1")[1])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = equal_len, ymin = -0.5, ymax = 0), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[1], color = RColorBrewer::brewer.pal(3, "Set1")[1])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = on_end, ymin = -1, ymax = -0.5), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[2], color = RColorBrewer::brewer.pal(3, "Set1")[2])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = equal_on, ymin = -1.5, ymax = -1), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[2], color = RColorBrewer::brewer.pal(3, "Set1")[2])+
  theme_classic()+
  geom_vline(xintercept = 12.54)+
  ylim(-1.5, 9.5)+
  labs(title = "Ways to Segement EPSP Stim")
```



```{r}
temp <- trace_list$EPSP

downsample_data(df = temp, len = 5000) %>% 
  gather(key, value, c("In9", "In12")) %>% 
  ungroup() %>% 
  mutate(key = factor(.$key, levels = c("In9", "In12"))) %>% 
  ggplot(aes(Time, value, group = Sweep))+
  geom_line()+
  facet_wrap(key~., scales = "free_y", ncol = 1)



#r11 == ~15.3
#r1 == ~17.9

place_params_for_predict_voltage_trace(tau = 19.9, 
                                       Rin = 15.3)

i=1
place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == i, ], 
                                       Time.ch = "Time", 
                                       Inj.ch = "In12")
  
run_predict_voltage_trace_py()
  
predicted_response <- retrieve_predicted_voltage()


ggplot()+
  geom_line(data = temp[temp$Sweep == i, ], aes(Time, In9), color = "red")+
  geom_line(data = predicted_response, aes(Time, predicted-68), color = "black")+
  labs(x = "Seconds", y = "mV")
      

  
```


#### Proof of principle: Contrasting simulaiton with LIF to regression and VIR
```{r}
M <- readABF_as_matrix2(path = 
                          paste0(abf_dir_path, "190915_0019.abf"),
                          # "C:/Users/Daniel/Documents/Trace_Holding/190915_0019.abf", #190924_0022.abf",
                   channels = "all",
                   relative.time = T)

temp <- as_tibble(M) %>% 
  janitor::clean_names(case = "upper_camel") %>% 
  mutate(Sweep = as.factor(Sweep)) %>% 
  group_by(Sweep) %>% 
  mutate(MinTime = min(Time, na.rm = T)) %>% 
  mutate(Time = Time - MinTime) %>% 
  filter(Sweep == 1) #%>% 
  # mutate(In7 = rollmean(In7, 17, fill = "extend"))


# temp %>% 
#   ggplot(aes(In7, In4))+
#   geom_path()+
#   geom_smooth(method = lm, fullrange = T, linetype = "dashed")+
#   theme_minimal()

fm <- lm(In4 ~ In7, data = temp)
fm_newdata <- data.frame(In4 = NA, 
                         In7 = temp$In7,
                         Time = temp$Time,
                         sweep = temp$Sweep)
fm_newdata$In4 <- predict(fm, newdata = fm_newdata)


temp <- temp[, c("Time", "In7", "In4")]

temp <- full_join(temp, rename(fm_newdata, lm = In4))

#TODO add in Rin / Tau programmatically

# 190915_0017 #-6nA
# 190915_0019 #epsp
# LC 5
# 
# Est. Rin: 51.21/6 = 8.535 MOhm
# Est. Taus: 
# Tau1			Tau2
# 58.482597351074219	11.020112037658691
# 21.417860031127930	N/A
place_params_for_predict_voltage_trace(tau = 21.417860031127930, Rin = 8.535)

place_data_for_predict_voltage_trace(input.df = temp, Time.ch = "Time", Inj.ch = "In7")

run_predict_voltage_trace_py()

predicted_response <- retrieve_predicted_voltage()



t1 <- temp
t2 <- as_tibble(predicted_response)

# # Feels hacky, but there seems to be a float rounding error here. E.g. Time 0.000199 != 0.0002
# t1$ms <- round(t1$Time * 10000)#/10000
# t2$ms <- round(t2$Time * 10000)#/10000
# 
# t1 <- t1 %>% dplyr::select(-Time)
# t2 <- t2 %>% dplyr::select(-Time)
# 
# t3 <- full_join(t1, t2) 

t3 <- cbind(t1, t2[, "predicted"]) 


t3$Vinf <- (t3$In7*8.535)-49.5
t3$predicted <- t3$predicted-49.5




plt_left <- 
t3 %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>% 
  ggplot(aes(Time, mV, color = Method))+
  geom_path()+
  geom_path(data = t3, aes(Time, In4), color = "black")+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)




t3_subtracted <- t3
t3_subtracted$lm <- t3_subtracted$In4 - t3_subtracted$lm
t3_subtracted$Vinf <- t3_subtracted$In4 - t3_subtracted$Vinf
t3_subtracted$predicted <- t3_subtracted$In4 - t3_subtracted$predicted
t3_subtracted$In4 <- t3_subtracted$In4 - -49.5

plt_mid <-
t3_subtracted %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>%
  ggplot(aes(Time, mV, color = Method))+
  geom_path()+ #TODO It seems there is a nA that's causing early termination here?
  geom_path(data = t3_subtracted, aes(Time, In4), color = "black")+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)

plt_right <- 
t3 %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>% 
  ggplot(aes(In4, mV, color = Method))+
  geom_path()+
  geom_abline(intercept = 0, slope = 1)+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)
  

(plt_left | plt_mid | plt_right) + plot_layout(widths = c(3, 3, 2))

```


###HTK/A
```{r}

```




#### </ begin copy from 02ExtractEphysData.Rmd >


## IHTK
  1. plot to get user to say which to drop (if there is no file with this info) # done
  2. smooth # done
  3. get peak values # done
4. get sustained values
  5. subtract off leak # done
  6. report values and leak # done
```{r}
trace <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace <- janitor::clean_names(as.data.frame(trace), case = "big_camel")
trace <- trace %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace <- trace %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# gather(trace, channel, mV, c("In4", "In9")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.25, 0.3)
# 
# gather(trace, channel, mV, c("In7", "In12")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.27, 0.28)

trace <- trace %>% ungroup()

peaks <- trace %>% group_by(Sweep) %>% filter(RelativeTime > 0.27 & RelativeTime < 0.28) %>% summarise(max.val = max(In7)) %>%
  ungroup()


peaks$mV <- NA
for (i in seq(1, nrow(peaks), 1)){
  Sweep <- peaks[i, "Sweep"] %>% as.numeric()
  
  peaks[i, "mV"] <- trace[trace$Sweep == Sweep &
                            trace$RelativeTime > 0.27 &
                            trace$RelativeTime < 0.28 &
                            trace$In7 == as.numeric(peaks[peaks$Sweep == Sweep, "max.val"]), "In4"] %>% as.numeric() %>% mean(na.rm = T)
}



fm <- lm(max.val ~ mV, filter(peaks, mV < -41))

peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
peaks <- peaks %>% mutate(leak.sub = max.val - leak)


ggplot(peaks)+
  # geom_smooth(method = "lm")+
  lemon::geom_pointline(aes(x = mV, max.val))+
  lemon::geom_pointline(aes(x = mV, leak), color = "red")+
  lemon::geom_pointline(aes(x = mV, leak.sub), color = "blue")
  

# go through sweeps plotting each and asking if the user wants to keep each one. Then return a df with the ones to keep
checkSweeps <- function(
  trace = trace,
  v.ch = "In4",
i.ch = "In7",
t.ch = "RelativeTime"
){
  use.sweeps <- data.frame(Sweep = unique(trace$Sweep),
                         Use = rep(F, times = length(unique(trace$Sweep))))
trace <- as.data.frame(trace)
for (i in seq_along(unique(trace$Sweep))){
  # use.sweep <- F
  # par(mfrow = c(1, 2))
  par(mfrow = c(2, 1))
  # with({
  plot(trace[trace$Sweep == i, v.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l", 
       xlab="", ylab="",
       main = paste("Sweep",as.character(i)))
  plot(trace[trace$Sweep == i, i.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l",
       xlab="", ylab="")
  # })
  
  for (j in 1:3){
    print(paste0("Retain sweep ", as.character(i),"?"))
    print("T/F or E to Exit")
    
    user.input <- readline(prompt = ">")
    
    
    if (user.input == "E" | user.input == "e"){
      break()
      
    } else if (user.input == "T" | user.input == "t"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- T
      break()
      
    } else if (user.input == "F" | user.input == "f"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- F
      break()
      
    } else {
      print(paste("Response not recognized.", as.character(j), "attempts remain."))
    }
    
    
  }
  if (user.input == "E" | user.input == "e"){
    break()
  }
}
return(use.sweeps)
}



```


## IA
  1. plot to get user to say which to drop (if there is no file with this info)
  2. subract user supplied IHTK (don't smooth or filter, but drop any traces that aren't present for both)
  3. smooth
  4. get peak values
  5. get sustained values
 
```{r}
trace.htk <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace.htk <- janitor::clean_names(as.data.frame(trace.htk), case = "big_camel")
trace.htk <- trace.htk %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.htk <- trace.htk %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()



trace.a <-
readABF_as_matrix(
  path = paste0(path.base, file.a)
  )

trace.a <- janitor::clean_names(as.data.frame(trace.a), case = "big_camel")
trace.a <- trace.a %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.a <- trace.a %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# subtract traces
subtract_traces <- function(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
){
  # htk.data = trace.htk.data %>% head()
  # a.data = trace.a %>% head()
  # Time = "Time"
  # rel.time = "RelativeTime"
  # Sweep = "Sweep"
  # current.chs = c("In7", "In12")
  
  htk.data <- as.data.frame(htk.data)
  a.data <- as.data.frame(a.data)
  
  if (length(htk.data[[current.chs[1]]]) != length(a.data[[current.chs[1]]])){
    warning("Dataframe nrows are not equal!\nReturning nothing")
    return()
  } else {
    for (i in seq_along(current.chs)){
      a.data[[current.chs[i]]] <- a.data[[current.chs[i]]] - htk.data[[current.chs[i]]]
    }
    return(a.data)
  }
}



trace.a.ls <- subtract_traces(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
)


# Get max for a time window
find_local_max <- function(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
){
  # trace = trace.a.ls
  # window.start = 0.27
  # window.stop  = 0.28
  # Sweep = "Sweep"
  # RelativeTime = "RelativeTime"
  # i.ch = "In7"
  # v.ch = "In4"
  
  peaks <- trace %>% 
    group_by(Sweep) %>% 
    filter(RelativeTime > window.start & RelativeTime < window.stop) %>% 
    summarise(max.val = max(get(i.ch))) %>% 
    ungroup()
  
  peaks$mV <- NA
  for (i in seq(1, nrow(peaks), 1)){
    Sweep1 <- peaks[i, Sweep] %>% as.numeric()
    
    peaks[i, "mV"] <- trace[trace$Sweep == Sweep1 &
                              trace$RelativeTime > window.start &
                              trace$RelativeTime < window.stop &
                              trace[[i.ch]] == as.numeric(peaks[peaks$Sweep == Sweep1, "max.val"]), v.ch] %>% as.numeric() %>% mean(na.rm = T)
  }
  
  return(peaks)
}



max.a.ls <- 
find_local_max(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)



### comparisons
max.a <- 
find_local_max(
  trace = trace.a,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)


max.htk <- 
find_local_max(
  trace = trace.htk,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)

# Leak subtract max values
subtract_leak <- function(peaks = max.htk, # output from find_local_max
                          min.mV = -81,
                          max.mV = -39){
  # peaks = max.htk # output from find_local_max
  # min.mV = -81
  # max.mV = -39
  fm <- lm(max.val ~ mV, filter(peaks, mV <= max.mV & mV >= min.mV))
  
  peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
  peaks <- peaks %>% mutate(leak.sub = max.val - leak)
  return(peaks)
}


max.htk.ls <- subtract_leak(peaks = max.htk, # output from find_local_max
                            min.mV = -81,
                            max.mV = -39)


ggplot()+
  lemon::geom_pointline(data = max.htk, aes(x = mV, max.val), color = "#fc9272")+
  lemon::geom_pointline(data = max.htk.ls, aes(x = mV, leak.sub), color = "#de2d26")+
  lemon::geom_pointline(data = max.a, aes(x = mV, max.val), color = "#9ecae1")+
  lemon::geom_pointline(data = max.a.ls, aes(x = mV, max.val), color = "#3182bd")



```



