---
title: "Produce Dataset"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(here)
library(tidyverse)
library(janitor)

library(zoo)
library(readABF)

library(broom)
library(minpack.lm) # getting Tau
library(patchwork)
library(ggsci)
library(cowplot)
library(patchwork)

library(gdata) # for humanReadable

library(minpack.lm) # for use in fit_tau_1term_exp()

theme_set(ggplot2::theme_minimal())


library(devtools)
devtools::load_all()
```

## Forward 
This file represents the full preparation of data. Ideally, where we pull processed data (e.g. where I've manually extraced values in clamp fit) will ultimately be replaced with automated, repeatable, and auditable processing. Auditing will be accomplished by including and option to write graphs of the input/output. 

```{r}
# TODO replace manual processing with automatic
# TODO Generate audit output
# TODO edit metadata file so as to allow for specification of traces or regions of traces to be excluded from a file (e.g. drop a segment with loss of voltage clamp)
```

## Build metadata

```{r global params}
use.file.path <- here("inst", "extdata", "ManualDataEphys02.xlsx")

abf_dir_path <- "D:/0000_Traces_mRNA24hLC/"

force_process_ABF <- c("000000_0000.abf")
```

# Working off of non-processed data ----

## Find all the relevant files
```{r}
metadata <- read_excel(use.file.path, sheet = "MetadataEphys")  
# update_type_names <- as_tibble(t(matrix(
#   c("htk", "htk", # ion
#     "a", "a",
#     "htkc", "htkc",
#     "ac", "ac",
#     
#     "tevc", "gjvc", # gj, Rs
#     "igj", "gjcc",
#     "igj_50", "gjcc",
#     
#     "fi_50", "fi", # excitability
#     "fi", "fi",
#     "epsp", "epsp",
#     "epsp_50", "epsp",
#     
#     "gj", "Unknown" #FIXME what are these?
#   ), nrow = 2)))
# names(update_type_names) <- c("InFile", "NewType")
```

## Check on hand abfs
```{r}
# Check for missing files relative to the abf directory

# Find all the traces specified in the metadata file (i.e. where type is not NA) and check to see if they exist in the `abf_dir`

absent_traces <- metadata[!is.na(metadata$Type), ]
absent_traces$Exists <- F

abf_dir <- list.files(abf_dir_path)
for (i in seq(1, nrow(absent_traces))){
  # make the file name
  num_zeros <- 4-nchar(absent_traces[i, "Recording"])
  num_zeros <- case_when(num_zeros == 0 ~ "",
                         num_zeros == 1 ~ "0",
                         num_zeros == 2 ~ "00",
                         num_zeros == 3 ~ "000")
  
  abf_name <- paste(as.character(absent_traces[i, "Experiment"]),
                    paste0(num_zeros, as.character(absent_traces[i, "Recording"]), ".abf"), 
                    sep = "_")
  # check if it exists in the dir
  absent_traces[i, "Exists"] <- abf_name %in% abf_dir
  
  # print(abf_name)
}

absent_traces_to_find <- absent_traces %>% 
  filter(Exists == F) %>% 
  mutate(RecordingLeadZeros = case_when((4 - nchar(Recording)) == 0 ~ "",
                                        (4 - nchar(Recording)) == 1 ~ "0",
                                        (4 - nchar(Recording)) == 2 ~ "00",
                                        (4 - nchar(Recording)) == 3 ~ "000")) %>% 
  mutate(FileName = paste0(Experiment, "_", RecordingLeadZeros, Recording, ".abf"))
```


Finding missing ABFs on the shared drive w/o Microsoft's search
```{r}
# Indexing all the ABFs in my directory on the shared drive is time consumming (~55 minutes over the VPN). It should only be done when an index doesn't exist already of if there's reason to beleave the index is no longer accurate. 
if (!file.exists(here("inst", "extdata", "shared_drive_abf_index.csv"))){
  start_loc <- "S:/Data_Daniel"
  
  tic <- Sys.time()
  all_abfs <- list.files("S:/Data_Daniel", "*.abf", recursive = T)
  toc <- Sys.time()
  print(toc - tic)
  
  write.csv(as.data.frame(all_abfs), file = here("inst", "extdata", "shared_drive_abf_index.csv"))
  rm(list = "all_abfs")
} 
all_abfs_on_shared_drive <- read.csv(here("inst", "extdata", "shared_drive_abf_index.csv"))
```


```{r}
all_abfs_on_shared_drive <- all_abfs_on_shared_drive %>% 
  as_tibble() %>% 
  mutate(all_abfs = as.character(all_abfs))

broken_path <- str_split(all_abfs_on_shared_drive$all_abfs, pattern = "/")

all_abfs_on_shared_drive$FileName <- map_chr(
  seq_along(broken_path), function(i){
  broken_path[[i]][[length(broken_path[[i]])]]
})


# if there's a match pull the path
absent_traces_to_find$PathOnShared <- NA

for (i in 1:nrow(absent_traces_to_find)){
  if(as.character(absent_traces_to_find[i, "FileName"]) %in% all_abfs_on_shared_drive$FileName){
    # get path
    absent_traces_to_find[i, "PathOnShared"] <- all_abfs_on_shared_drive[all_abfs_on_shared_drive$FileName == as.character(absent_traces_to_find[i, "FileName"]), "all_abfs"]

  } else {
    absent_traces_to_find[i, "PathOnShared"] <- NA
  }
}

# move from server
absent_traces_to_find$moved <- F
# Check for file's existence, if it's there move it and tag it as moved.
for (i in 1:nrow(absent_traces_to_find)){
  if(!is.na(absent_traces_to_find[i, "PathOnShared"])){
    file_to_move <- paste0("S:/Data_Daniel", "/", as.character(absent_traces_to_find[i, "PathOnShared"]))
    
    if (file.exists(file_to_move)){
      file.copy(
        from = file_to_move,
        to = paste0(
          abf_dir_path,
          absent_traces_to_find[i, "FileName"]  
        )
      )
      
      absent_traces_to_find[i, "moved"]  <- T
    }
  }
}

# After everything's moved, manually search for the rest. 

manually_find <- absent_traces_to_find %>% 
  filter(moved == F) %>% 
  select(Experiment, Page, Recording, Type, TEA, Condition, FileName)
write.csv(manually_find, file = here("data", "manually_find_ABFs.csv"))


# Can't seem to find experiment 190917a
# looking at manually processed data I don't see any evidence of it. Possibly it didn't get moved to the shared drive? 
#FIXME go and check the lab computer to make sure the missing file isn't there. 
metadata <- metadata[metadata$Experiment != "190917a", ]
```

```{r depricated}
# 
# 
# abf_names <- str_extract_all(all_abfs_on_shared_drive$all_abfs, "[[^/]]*[[:punct:]]abf$")
# 
# all_abfs_on_shared_drive$abf_names <- abf_names
# 
# 
# 
# # lapply(mtcars, function(x){x[length(x)]})
# 
# 
# i=1
# as.character(absent_traces_to_find[i, "FileName"]) %in% unlist(all_abfs_on_shared_drive$abf_names)
# 
# 
# # > file_groups
# #    Experiment       Group
# # 1      190924    Baseline
# # 2     190924a    Baseline
# # 3      190926    Baseline
# # 4      190927    Baseline
# # 5     190927a    Baseline
# # 6      190930    Baseline
# # 7     190930a    Baseline
# # 8     190808a Compensated
# # 9      190830 Compensated
# # 10     190904 Compensated
# # 11     191001 Compensated
# # 12     191004 Compensated
# # 13     190903     Delayed
# # 14     190905     Delayed
# # 15     190906     Delayed
# # 16     190907     Delayed
# # 17     190915     Delayed
# # 18     190917     Delayed
# # 19     190918     Delayed
# 
# 
# abf_names <- str_extract_all(all_abfs_on_shared_drive$all_abfs, "[[^/]]*[[:punct:]]abf$")
# 
# all_abfs_on_shared_drive$abf_names <- abf_names
# 
# times_matched <- unlist(map(seq(1, nrow(all_abfs_on_shared_drive)), function(i){
#   # if it matches at least once the sum will be >0. It should match at most once.
#   times.matched <- sum(unlist(map(file_groups$Experiment, function(prefix){
#     str_detect(all_abfs_on_shared_drive$abf_names[[i]], paste0(as.character(prefix), "_")) # adding a terminal _ to the search string will prevent 000000a from matching to both 000000 and itself.
#   })))
# 
#   return(times.matched)
# }))
# 
# all_abfs_on_shared_drive$times_matched <- times_matched
# 
# # Looks like it's working as expected
# if (max(times_matched) > 1){
#   all_abfs_on_shared_drive[all_abfs_on_shared_drive$times_matched == max(times_matched), ]
# }
# 
# # matches
# all_abfs_match <- all_abfs_on_shared_drive[all_abfs_on_shared_drive$times_matched == 1, ]
# 
# all_abfs_match$size  <- NA
# all_abfs_match$mtime <- as.POSIXct(NA)
# all_abfs_match$ctime <- as.POSIXct(NA)
# all_abfs_match$atime <- as.POSIXct(NA)
# 
# for (i in seq(1, nrow(all_abfs_match))){
#   current_info <- file.info(paste(start_loc, all_abfs_match[i, "all_abfs"], sep = "/") )
# 
#   all_abfs_match[i, "size"]  <- current_info$size
#   all_abfs_match[i, "mtime"] <- current_info$mtime # file modification
#   all_abfs_match[i, "ctime"] <- current_info$ctime # last status change
#   all_abfs_match[i, "atime"] <- current_info$atime # last access time
# }
# 
# 
# all_abfs_match$abf_names <- all_abfs_match$abf_names %>% unlist()
# 
# 
# # find duplicated abfs
# dupe_abfs <- all_abfs_match %>%
#   select(abf_names) %>%
#   group_by(abf_names) %>%
#   tally() %>%
#   filter(n > 1)
# 
# all_abfs_match$keep <- F
# # Keep all non duplicates
# all_abfs_match[!(all_abfs_match$abf_names %in% as.character(dupe_abfs$abf_names)), "keep"] <- T
# 
# for (i in seq(1, nrow(dupe_abfs))){
#   # if same size, keep oldest
#   if (length( unique( all_abfs_match[all_abfs_match$abf_names == as.character(dupe_abfs[i, "abf_names"]), "size"] ) ) == 1){
#     # unless they're the same, then keep the first.
#     if (length( unique(all_abfs_match[all_abfs_match$abf_names == as.character(dupe_abfs[i, "abf_names"]), "mtime"]) ) == 1){
#       all_abfs_match[all_abfs_match$abf_names == as.character(dupe_abfs[i, "abf_names"]), "keep"][1] <- T
#     } else {
#       warning(paste("Dupe", as.character(i), "has multiple times! Additional logic needed!"))
#       #TODO
#     }
#   } else {
#       warning(paste("Dupe", as.character(i), "has unequal file sizes! Additional logic needed!"))
#   }
# }
# 
# 
# target_abfs <- all_abfs_match[all_abfs_match$keep == T & all_abfs_match$size < 13000000, ]
# # install.packages("gdata")
# target_abfs$size %>% sum() %>% gdata::humanReadable()
# 
# 
# local_abfs <- list.files("C:/Users/Daniel/Documents/Trace_Holding/", pattern = ".abf")
# target_abfs <- target_abfs[!(target_abfs$abf_names %in% local_abfs), ]
# 
# 
# # Copy
# for (i in seq(1, nrow(target_abfs))){
#   temp_path <- paste(start_loc, as.character(target_abfs[i, "all_abfs"]), sep = "/")
#   if (file.exists(temp_path)){
#     file.copy(from = temp_path,
#               to = "C:/Users/Daniel/Documents/Trace_Holding/")
#   } else {
#     warning(paste("Item", as.character(i), "does not exist!"))
#   }
# }
# 
```


## Standard Processing

```{r}
metadata <- metadata %>% 
  mutate(ABFType = case_when(Type %in% c("tevc") ~ "gjvc",
                            Type %in% c("igj","igj_50", "gj") ~ "gjcc",
                            Type %in% c("epsp", "epsp_50") ~ "epsp",
                            Type %in% c("fi_50", "fi") ~ "fi"))

abfs_to_process <- metadata %>% 
  filter(ABFType %in% c("gjvc", "gjcc", "epsp", "fi")) %>% 
  filter(Condition %in% c("Baseline", "Compensated", "Delayed"))

# make expected file names
abfs_to_process <- abfs_to_process %>% 
  mutate(num_zeros = str_length(Recording)) %>% 
  mutate(num_zeros = ifelse(num_zeros == 1, "000", 
                            ifelse(num_zeros == 2, "00", 
                                   ifelse(num_zeros == 3, "0", NA)))) %>% 
  mutate(File = paste0(Experiment, "_", num_zeros, as.character(Recording), ".abf" )) %>% 
  select(-num_zeros)

```


```{r}
# Many experiments with duplicate recordings
abfs_to_process %>% 
  select(Experiment, ABFType, In4, In9, File) %>% 
  gather(key = "Channel", value = "Cell", c("In4", "In9")) %>% 
  group_by(Experiment, Cell, ABFType) %>% 
  tally()

abfs_to_process <- abfs_to_process %>% 
  select(Experiment, ABFType, In4, In9, File) %>% 
  gather(key = "Channel", value = "Cell", c("In4", "In9")) %>% 
  mutate(Processed = F)





# # let's start with one experiment
# # arrange so that gjvc/gjcc are on top.
# abfs_one_exp <- abfs_to_process %>% 
#   filter(Experiment == "190808a") %>% #FIXME 
#   arrange(desc(ABFType), File)
# 
# abfs_one_ABF <- abfs_one_exp[abfs_one_exp$File == "190808a_0018.abf", ]

# current_file <- as.character(abfs_one_ABF[1, "File"])
# current_ABFType <- as.character(abfs_one_ABF[1, "ABFType"])

# Added cols for each 
#Ig   R1c
#"CC"          "R1"          "R11"         "R12"         "Rc"          "Tau_est"     "Tau_std.err" "Vrest"





```  

Process gjvcs
```{r}
tictoc::tic()

process_these_abfs <- abfs_to_process %>% filter(ABFType == "gjvc")

unique_abfs <- unique(process_these_abfs$File)


# unique_abfs[i]

# inelegant, but functional. 
unique_abfs <- unique_abfs[!(unique_abfs %in% c(
  "190903_0027.abf",
  
  "190904_0017.abf", #lm.fit
  "190904_0027.abf", #lm.fit
  
  "190906_0031.abf",
  "190906_0041.abf",
  
  "190915_0023.abf"
))]

# FIXME it seems that "190903_0027.abf" is being run even though it should be rejected\
 # Error in lm.fit(x, y, offset = offset, singular.ok = singular.ok, ...) : 
 #  0 (non-NA) cases 

for (i in seq_along(unique_abfs)){
  print(i)
  # process_these_abfs[process_these_abfs$File == unique_abfs[i], ]

  current_file <- as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "File"])[1])
  ## Should we process the current ABF? ====
  current_trace <- check_abf_expected(
    exempt_ABF = force_process_ABF, 
    dir_path = abf_dir_path,
    file_name = current_file,
    file_type = as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "ABFType"])[1])
  )
  
  
  if (current_trace$process){
    current_trace <- current_trace$trace
    
    
    out <- process_gjvc_trace(trace = current_trace)
    

          process_these_abfs[process_these_abfs$File == current_file & process_these_abfs$Channel == "In4", "Ig"] <-  out$df[1, "In4_to_In9"]
          process_these_abfs[process_these_abfs$File == current_file & process_these_abfs$Channel == "In9", "Ig"] <-  out$df[1, "In9_to_In4"]
          process_these_abfs[process_these_abfs$File == current_file & process_these_abfs$Channel == "In4", "R1c"] <- out$df[1, "In4_R1c"]
          process_these_abfs[process_these_abfs$File == current_file & process_these_abfs$Channel == "In9", "R1c"] <- out$df[1, "In9_R1c"]
          
          # Save for review: ####
          save_plot(here("data", "data_audits", "gjvc", paste(str_remove(current_file, ".abf"), "gjvc", "trace.pdf", sep = "-")),
                    out$diagnostic_plots$trace, base_height = 7, base_width = 10)
          
          save_plot(here("data", "data_audits", "gjvc", paste(str_remove(current_file, ".abf"), "gjvc", "fit.pdf", sep = "-")),
                    out$diagnostic_plots$fit, base_height = 7, base_width = 10)   
          
          # write.csv(out$df,
          #           here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjvc", "df.csv", sep = "-"))          )

    
  } 
}


tictoc::toc()

# merge back
abfs_to_process <- full_join(abfs_to_process, process_these_abfs)

```



Process gjccs
```{r}
tictoc::tic()

process_these_abfs <- abfs_to_process %>% filter(ABFType == "gjcc")

unique_abfs <- unique(process_these_abfs$File)

# inelegant, but functional. 
unique_abfs <- unique_abfs[!(unique_abfs %in% c(
"190830_0033.abf",
"190905_0018.abf",
"190906_0032.abf",
"190906_0050.abf",
 "190907_0014.abf",
"190918_0029.abf",
"190924_0021.abf",
"190924_0036.abf",
"190924_0037.abf",
"190926_0016.abf",
"190927a_0014.abf",
"190930_0012.abf",
"191001_0016.abf",
"191001_0017.abf"
 # Error in UseMethod("rename_") : 
 #  no applicable method for 'rename_' applied to an object of class "NULL" 
))]


# unique_abfs <- "191004_0027.abf"
# process_these_abfs <- filter(process_these_abfs, File == "191004_0027.abf") 

# Add cols to fill
process_these_abfs <- full_join(select(process_these_abfs, -Sweep), 
                                expand.grid(Experiment = process_these_abfs$Experiment, 
                                            Sweep = 1:5,
                                            CC = NA,
                                            R1 = NA,
                                            R11 = NA,
                                            R12 = NA,
                                            Rc = NA,
                                            Tau_est = NA,
                                            Tau_std.err = NA,
                                            Vrest = NA))



for (i in seq_along(unique_abfs)){
  print(i)
  # process_these_abfs[process_these_abfs$File == unique_abfs[i], ]

  current_file <- as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "File"])[1])
  ## Should we process the current ABF? ====
  current_trace <- check_abf_expected(
    exempt_ABF = force_process_ABF, 
    dir_path = abf_dir_path,
    file_name = current_file,
    file_type = as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "ABFType"])[1])
  )
  
  
  if (current_trace$process){
    current_trace <- current_trace$trace
    
    
    out <- process_gjcc_trace(trace = current_trace)
    
    out_df <- out$df 
    out_df <- out_df %>% 
      gather("key", "value", names(out_df)[names(out_df) != "Sweep"]) %>% 
      mutate(key = str_replace_all(key, "In4_", replacement = "In4-"),
             key = str_replace_all(key, "In9_", replacement = "In9-")) %>% 
      separate(col = key, sep = "-", into = c("Ch", "DV")) %>% 
      spread(key = "DV", value = "value") %>% 
      mutate(File = current_file,
             Sweep = as.numeric(Sweep)) %>% 
      rename(Channel = Ch)
    
    
    process_these_abfs <- full_join(process_these_abfs, out_df)

    # row_ids <- out_df %>% select(Sweep, Channel, File) %>% distinct()
    # # inefficient but functional -- merging isn't working properly
    # for (j in seq(1, nrow(row_ids))){
    #   t_sw <- unlist(row_ids[j, "Sweep"])
    #   t_ch <- unlist(row_ids[j, "Channel"])
    #   t_fl <- unlist(row_ids[j, "File"])
    #   
    #   for (param in c("CC", "R1", "R11", "R12", "Rc", "Tau_est", "Tau_std.err", "Vrest")){
    #     process_these_abfs[process_these_abfs$File == t_fl & process_these_abfs$Channel == t_ch & process_these_abfs$Sweep == t_sw, param] <- unlist(out_df[out_df$File == t_fl & out_df$Channel == t_ch & out_df$Sweep == t_sw, param])
    #   }
    # }
    
    
    # Save for review:
    # Estimates of Tau look poor.
    save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "trace.pdf", sep = "-")),
              out$diagnostic_plots$trace, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "segment.pdf", sep = "-")),
              out$diagnostic_plots$segment, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "fit_in4.pdf", sep = "-")),
              out$diagnostic_plots$fit_In4, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "fit_in9.pdf", sep = "-")),
              out$diagnostic_plots$fit_In9, base_height = 7, base_width = 10)
    
    
         

    
  } 
}

process_these_abfs <- distinct(process_these_abfs) %>% filter(!is.na(R11))
tictoc::toc()



# abfs_to_process <- full_join(abfs_to_process, 
#           process_these_abfs) 

# full_join(abfs_to_process, 
#           process_these_abfs) 
# 
# process_these_abfs[is.na(process_these_abfs$Experiment), ]
# 
# 
# t1 <- abfs_to_process %>% filter(File == "190808a_0019.abf")
# t2 <- process_these_abfs %>% filter(File == "190808a_0019.abf")
# 
# 
# full_join(t1, 
#           select(t2, 
#                  File, Channel, Sweep, CC, R1, R11, R12, Rc, Tau_est, Tau_std.err, Vrest)
#           ) %>% tail()



abfs_to_process <- full_join(
  abfs_to_process, 
  select(process_these_abfs, 
         File, Channel, Sweep, CC, R1, R11, R12, Rc, Tau_est, Tau_std.err, Vrest)
          )
# merge back
# abfs_to_process <- full_join(abfs_to_process, mutate(, Sweep = as.character(Sweep)))

```


### Backup Point
```{r}
save.image(file='myEnvironment.RData')
load('myEnvironment.RData')
```


#### Data review:

gjcc seems to predict bigger junctional conductance, R1 than gjvc would. 
```{r}
# abfs_to_process %>% 
abfs_to_process %>% 
  group_by(Experiment, Cell) %>% 
  mutate(Ig = median(Ig, na.rm = T),
         R1c = median(R1c, na.rm = T)) %>% #tail()
  ggplot(aes(x = Rc^-1, y = abs(Ig)))+
  geom_abline(slope = 1, intercept = 0, color = 'firebrick')+
  # geom_line(data = data.frame(x = seq(1, 50, length.out = 100), y = seq(1, 50, length.out = 100)),
  #                              aes(x=x,y=y), color = "firebrick")+
  geom_point()
  # coord_cartesian(x = c(0, 100))+
  # scale_x_log10()



abfs_to_process %>% 
  group_by(Experiment, Cell) %>% 
  mutate(Ig = median(Ig, na.rm = T),
         R1c = median(R1c, na.rm = T)) %>% #tail()
  unite(uid, Experiment, Cell) %>% 
  ggplot(aes(x = R1, y = R1c, group = uid))+
  # geom_line()+
  geom_point()+
  # geom_abline(slope = 1, intercept = 0, color = 'firebrick')+
  geom_line(data = data.frame(x = seq(1, 13, length.out = 100), 
                              y = seq(1, 13, length.out = 100),
                              uid = "a"),
  aes(x=x,y=y), color = "firebrick")+
  
  scale_x_log10()
  # coord_cartesian(x = c(0, 100))
```



```{r}
# DVs <- c("Ig", "R1c", "CC", "R1", "R11", "R12", "Rc", "Tau_est", "Tau_std.err", "Vrest")
# 
# 
# abfs_medians <- abfs_to_process
# 
# 
# abfs_to_process %>% 
#   select(-Processed) %>% 
#   group_by(Experiment, Cell) %>% 
#   mutate_at(DVs, median, na.rm = T)
# 
# 
# # Experiment is missing from a lot of the files
# # abfs_medians$Experiment <- unlist(transpose(str_split(abfs_medians$File, pattern = "_"))[1])
# 
# # abfs_medians <- abfs_medians %>% 
# #   ungroup() %>% 
# #   select(-Sweep, -ABFType, -Channel, -Processed) %>% 
# #   group_by(Experiment, File, Cell) %>%
# #   mutate_at(DVs, median, na.rm=T) %>%
# #   distinct() %>%
# #   ungroup() %>%
# #   select(-File) %>%
# #   group_by(Experiment, Cell) %>%
# #   mutate_at(DVs, median, na.rm=T) %>%
# #   ungroup() %>%
# #   distinct()
# 
# 
# abfs_medians %>% View
#   

#TODO what is the distance between the automatically and manualy measured values?  
```


```{r}
#TODO Add in manually measured taus for each cell with unreasonable data. 


abfs_to_process

```



```{r}
#FIXME make sure all the inputs are clean before batch processing epsp/fi

abfs_to_process
```

Repeat pattern for epsp

```{r}
tictoc::tic()

process_these_abfs <- abfs_to_process %>% filter(ABFType == "epsp")

unique_abfs <- unique(process_these_abfs$File)


# inelegant, but functional. 
unique_abfs <- unique_abfs[!(unique_abfs %in% c(

))]


unique_abfs <- "190808a_0014.abf"
current_cell_params <- filter(abfs_to_process, Experiment == "190808a", Cell == 4) %>% #FIXME
  summarise(
    Experiment = Experiment,
    Cell = Cell,
    Channel = Channel,
    Rin = median(R11, na.rm = T),
    Tau = median(Tau_est, na.rm = T)) %>% 
  distinct()

# # A tibble: 1 x 5
#   Experiment  Cell Channel   Rin   Tau
#   <chr>      <dbl> <chr>   <dbl> <dbl>
# 1 190808a        4 In4      14.3 -11.8



for (i in seq_along(unique_abfs)){
  print(i)
  
  current_file <- as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "File"])[1])
  ## Should we process the current ABF? ====
  current_trace <- check_abf_expected(
    exempt_ABF = force_process_ABF,
    dir_path = abf_dir_path,
    file_name = current_file,
    file_type = as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "ABFType"])[1])
  )
  
  
  if (current_trace$process){
    current_trace <- current_trace$trace
    
    if (unlist(current_cell_params[, "Channel"]) == "In4"){
      out <- predict_epsp_responses(trace = current_trace,
                                    tau = abs(as.numeric(unlist(current_cell_params[, "Tau"]))),
                                    rin = as.numeric(unlist(current_cell_params[, "Rin"])),
                                    v_ch = "In4",
                                    i_ch = "In7")
      
      # Save for review:
      saveRDS(current_trace[, c("In4", "In7", "Sweep", "Time")], 
              here("data", "predicted_voltage", paste(
                str_remove(current_file, ".abf"), "epsp", "In4", "actual_v.rds", sep = "-")))
      
      saveRDS(out$predictions, 
              here("data", "predicted_voltage", paste(
                str_remove(current_file, ".abf"), "epsp", "In4", "predict_v.rds", sep = "-")))
      
      
      
       
      save_plot(here("data", "data_audits", "epsp", paste(
        str_remove(current_file, ".abf"), "epsp", "In4", "segment.pdf", sep = "-")),
        out$diagnostic_plots$trace, base_height = 7, base_width = 10)
      
      
    } else if (unlist(current_cell_params[, "Channel"]) == "In9"){
      out <- predict_epsp_responses(trace = current_trace,
                                    tau = abs(as.numeric(unlist(current_cell_params[, "Tau"]))),
                                    rin = as.numeric(unlist(current_cell_params[, "Rin"])),
                                    v_ch = "In9",
                                    i_ch = "In12")
      
      # Save for review:
      saveRDS(current_trace[, c("In9", "In12", "Sweep", "Time")], 
              here("data", "predicted_voltage", paste(
                str_remove(current_file, ".abf"), "epsp", "In4", "actual_v.rds", sep = "-")))
      
      saveRDS(out$predictions, 
              here("data", "predicted_voltage", paste(
                str_remove(current_trace, ".abf"), "epsp", "In9", "predict_v.rds", sep = "-")))
      
      save_plot(here("data", "data_audits", "epsp", paste(
        str_remove(current_trace, ".abf"), "epsp", "In9", "segment.pdf", sep = "-")),
        out$diagnostic_plots$trace, base_height = 7, base_width = 10)
    }
  }
}


tictoc::toc()

# for (i in seq_along(unique_abfs)){
#   print(i)
#   # process_these_abfs[process_these_abfs$File == unique_abfs[i], ]
# 
#   current_file <- as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "File"])[1])
#   ## Should we process the current ABF? ====
#   current_trace <- check_abf_expected(
#     exempt_ABF = force_process_ABF, 
#     dir_path = abf_dir_path,
#     file_name = current_file,
#     file_type = as.character(unlist(process_these_abfs[process_these_abfs$File == unique_abfs[i], "ABFType"])[1])
#   )
#   
#   
#   if (current_trace$process){
#     current_trace <- current_trace$trace
#     
#     
#     out <- process_gjcc_trace(trace = current_trace)
#     
#     out_df <- out$df 
#     out_df <- out_df %>% 
#       gather("key", "value", names(out_df)[names(out_df) != "Sweep"]) %>% 
#       mutate(key = str_replace_all(key, "In4_", replacement = "In4-"),
#              key = str_replace_all(key, "In9_", replacement = "In9-")) %>% 
#       separate(col = key, sep = "-", into = c("Ch", "DV")) %>% 
#       spread(key = "DV", value = "value") %>% 
#       mutate(File = current_file,
#              Sweep = as.numeric(Sweep)) %>% 
#       rename(Channel = Ch)
#     
#     
#     process_these_abfs <- full_join(process_these_abfs, out_df)
# 
#     
#     
#     
#     # Save for review:
#     # Estimates of Tau look poor.
#     save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "trace.pdf", sep = "-")),
#               out$diagnostic_plots$trace, base_height = 7, base_width = 10)
#     
#     save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "segment.pdf", sep = "-")),
#               out$diagnostic_plots$segment, base_height = 7, base_width = 10)
#     
#     save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "fit_in4.pdf", sep = "-")),
#               out$diagnostic_plots$fit_In4, base_height = 7, base_width = 10)
#     
#     save_plot(here("data", "data_audits", "gjcc", paste(str_remove(current_file, ".abf"), "gjcc", "fit_in9.pdf", sep = "-")),
#               out$diagnostic_plots$fit_In9, base_height = 7, base_width = 10)
#     
#     
#          
# 
#     
#   } 
# }
# 
# process_these_abfs <- distinct(process_these_abfs) %>% filter(!is.na(R11))
# tictoc::toc()
# 
# 
# 
# # abfs_to_process <- full_join(abfs_to_process, 
# #           process_these_abfs) 
# 
# full_join(abfs_to_process, 
#           process_these_abfs) 
# 
# process_these_abfs[is.na(process_these_abfs$Experiment), ]
# 
# 
# t1 <- abfs_to_process %>% filter(File == "190808a_0019.abf")
# t2 <- process_these_abfs %>% filter(File == "190808a_0019.abf")
# 
# 
# full_join(t1, 
#           select(t2, 
#                  File, Channel, Sweep, CC, R1, R11, R12, Rc, Tau_est, Tau_std.err, Vrest)
#           ) %>% tail()
# 
# 
# 
# abfs_to_process <- full_join(
#   abfs_to_process, 
#   select(process_these_abfs, 
#          File, Channel, Sweep, CC, R1, R11, R12, Rc, Tau_est, Tau_std.err, Vrest)
#           )
# # merge back
# # abfs_to_process <- full_join(abfs_to_process, mutate(, Sweep = as.character(Sweep)))

```


workspace -- getting metrics from epsp
```{r}
# read in trace
brian2_trace_files <- list.files(here("data", "predicted_voltage"))

brian2_trace_sets <- brian2_trace_files %>% 
  str_remove(pattern = "-actual_v.rds") %>% 
  str_remove(pattern = "-predict_v.rds") %>% 
  unique()

i=1 #FIXME for i in seq all sets
brian2_read_in <- brian2_trace_files[str_detect(brian2_trace_files, brian2_trace_sets[i])]


temp <- map(brian2_read_in, function(read_file){
  temp_predict <- readRDS(here("data", "predicted_voltage", read_file))
  
  if(str_detect(read_file, pattern = "predict_v")){
  #consolidate into one df
  for (j in seq(1, length(temp_predict))){
    temp_predict[[j]]$Sweep <- j
  }
  temp_predict <- do.call(rbind, temp_predict)
  }
  return(temp_predict)
})

names(temp) <- brian2_read_in

temp_a <- temp[str_detect(names(temp), pattern = "actual_v")][[1]]
temp_p <- temp[str_detect(names(temp), pattern = "predict_v")][[1]] %>% as.data.frame() %>% as_tibble()
temp_a$nrow <- seq(1, nrow(temp_a))
temp_p$nrow <- seq(1, nrow(temp_p))
temp_a$Sweep <- as.character(temp_a$Sweep)
temp_p$Sweep <- as.character(temp_p$Sweep)

temp <- full_join(temp_a, select(temp_p, -Time)) %>% select(-nrow)




downsample_data(temp, len = 10000) %>% 
# temp %>% 
  mutate(predicted = predicted - offset) %>% 
  mutate(difference = In4-predicted) %>% 
  ggplot(aes(x = Time))+
  geom_ribbon(aes(ymin=In4, ymax=predicted), fill = "cornflowerblue")+
  geom_line(aes(y=In4), color = "black")+
  geom_line(aes(y=predicted), color = "cornflowerblue", alpha = 0.3)+
  # geom_line(aes(y=difference-offset), color = "purple")+
  facet_grid(Sweep~.)


temp_part1 <- temp %>% 
  mutate(predicted = predicted - offset) %>% 
  mutate(difference = In4-predicted) %>% 
  gather(Key, mV, c("In4", "predicted", "difference")) %>% 
  group_by(Key, Sweep) %>% 
# Min Voltage
  mutate(Min.V = min(mV, na.rm = T)) %>%
  # Baseline voltage
  # Defining as average of the lowest 20% of points
  mutate(Use.in.Base = quantile(mV, probs = .2, na.rm = T)) %>%
  mutate(Use.in.Base = ifelse(mV <= Use.in.Base,
    mV,
    NA
  )) %>%
  mutate(Use.in.Base = mean(Use.in.Base, na.rm = T)) %>%
  # Max voltage
  mutate(Max.V = max(mV, na.rm = T)) %>%
  # Median Voltage
  mutate(Med.V = median(mV, na.rm = T)) %>%
  # Mean Voltage
  mutate(Mean.V = mean(mV, na.rm = T)) %>%
    # # Duration
    # mutate(Max.Time = max(Time, na.rm = T)) %>% 
  # AUC
  # Using Min.V
  mutate(AUC = (mV - Min.V))


# AUC
# Median mV
# Mean mV
# Stimulus correlation
# Max mV


```
















Placeholder for fi






























```{r}

## If we decided to, then process it. ====
if (process_current_ABF) {
  if (current_ABFType == "gjvc"){

    
###############################################################################
    #TODO I was working here to convert the below into a feasable batch processing.
    # need to store results for the duration of working on a single experiment at least (then they can be written out)
    # need to make sure the data is tidy and replicates are dealt with. 
    # need to test it
    
    out <- process_gjvc_trace(trace = temp_trace)
    
    abfs_one_exp[abfs_one_exp$File == current_file & abfs_one_exp$Channel == "In4", "Ig"] <-  out$df[1, "In4_to_In9"]
    abfs_one_exp[abfs_one_exp$File == current_file & abfs_one_exp$Channel == "In9", "Ig"] <-  out$df[1, "In9_to_In4"]
    abfs_one_exp[abfs_one_exp$File == current_file & abfs_one_exp$Channel == "In4", "R1c"] <- out$df[1, "In4_R1c"]
    abfs_one_exp[abfs_one_exp$File == current_file & abfs_one_exp$Channel == "In9", "R1c"] <- out$df[1, "In9_R1c"]

    # Save for review: ####
    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjvc", "trace.pdf", sep = "-")),
              out$diagnostic_plots$trace, base_height = 7, base_width = 10)

    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjvc", "fit.pdf", sep = "-")),
              out$diagnostic_plots$fit, base_height = 7, base_width = 10)   
    
    # write.csv(out$df,
    #           here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjvc", "df.csv", sep = "-"))          )

    
  } else if (current_ABFType == "gjcc"){
    
    out <- process_gjcc_trace(trace = temp_trace)
    
    
    out_df <- out$df %>% 
      gather("key", "value", names(temp)[names(temp) != "Sweep"]) %>% 
      mutate(key = str_replace_all(key, "In4_", replacement = "In4-"),
             key = str_replace_all(key, "In9_", replacement = "In9-")) %>% 
      separate(col = key, sep = "-", into = c("Ch", "DV")) %>% 
      spread(key = "DV", value = "value") %>% 
      mutate(File = current_file)
    
    abfs_one_exp <- full_join(abfs_one_exp, out_df)
    
    # Save for review:
    # Estimates of Tau look poor.
    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjcc", "trace.pdf", sep = "-")),
              out$diagnostic_plots$trace, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjcc", "segment.pdf", sep = "-")),
              out$diagnostic_plots$segment, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjcc", "fit_in4.pdf", sep = "-")),
              out$diagnostic_plots$fit_In4, base_height = 7, base_width = 10)
    
    save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjcc", "fit_in9.pdf", sep = "-")),
              out$diagnostic_plots$fit_In9, base_height = 7, base_width = 10)
    
    # write.csv(out$df,
    #           here("data", "data_audits", paste(str_remove(input_file, ".abf"), "gjcc", "df.csv", sep = "-")))

    
  } 
```


Get expected voltage response 
```{r}
  if (current_ABFType == "fi"){
#   #TODO retrieve Rin/tau
    #TODO what do we do if there are multiple estimates of a tau/rin?
    
    predict_fi_responses
    temp_trace
    return(list(diagnostic_plots = list(traces = my_plts),
                predictions = predicted_response_list))
    # # Save for review:
    # input_file <- "190903_0025.abf"
    
    # saveRDS(predicted_response_list, 
    #         here("data", "predicted_voltage", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))
    # 
    # save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "multi_plt.pdf", sep = "-")),
    #           multi_plt, base_height = 7, base_width = 10)
    
    # test_load <- readRDS(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))  # # Save for review:
#     # input_file <- "190903_0025.abf"
#     
#   #TODO retrieve Rin/tau
    #TODO what do we do if there are multiple estimates of a tau/rin?
    
    out <- predict_epsp_responses(temp_trace)
    
    out$diagnostic_plots$trace
    out$predictions
    
    # saveRDS(out$predictions, 
    #         here("data", "predicted_voltage", paste(str_remove(input_file, ".abf"), "epsp", "predict_v.rds", sep = "-")))
    
    # save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "epsp", "segment.pdf", sep = "-")),
    #           out$diagnostic_plots$trace, base_height = 7, base_width = 10)  # saveRDS(predicted_response_list, 
#     #         here("data", "predicted_voltage", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))
#     # 
#     #TODO what do we do if there are multip#     # save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "multi_plt.pdf", sep = "-")),
#     #           multi_plt, base_height = 7, base_width = 10)
#     
#     # test_load <- readRDS(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))
#     
#   } else if (current_ABFType == "epsp"){
#     #TODO retrieve Rin/tau
#     #TODO what do we do if there are multiple estimates of a tau/rin?
#     
#     out <- predict_epsp_responses(temp_trace)
#     
#     out$diagnostic_plots$trace
#     out$predictions
#      else if (current_ABFType
    #TODO retrieve Rin/tau
    #TODO what do we do if there are multiple estimates of a tau/rin?
    
    predict_fi_responses
    temp_trace
    return(list(diagnostic_plots = list(traces = my_plts),
                predictions = predicted_response_list))
    # # Save for review:
    # input_file <- "190903_0025.abf"
    
    # saveRDS(predicted_response_list, 
    #         here("data", "predicted_voltage", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))
    # 
    # save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "multi_plt.pdf", sep = "-")),
    #           multi_plt, base_height = 7, base_width = 10)
    
    # test_load <- readRDS(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "fi", "predict_v.rds", sep = "-")))
    
  } else if (current_ABFType == "epsp"){
    #TODO retrieve Rin/tau
    #TODO what do we do if there are multiple estimates of a tau/rin?
    
    out <- predict_epsp_responses(temp_trace)
    
    out$diagnostic_plots$trace
    out$predictions
    
    # saveRDS(out$predictions, 
    #         here("data", "predicted_voltage", paste(str_remove(input_file, ".abf"), "epsp", "predict_v.rds", sep = "-")))
    
    # save_plot(here("data", "data_audits", paste(str_remove(input_file, ".abf"), "epsp", "segment.pdf", sep = "-")),
    #           out$diagnostic_plots$trace, base_height = 7, base_width = 10)
    
  } 
  
}
```




































## Loop over all desired files and extract the relevant metrics. 
```{r}
#TODO remove the proof of principle when the demo vignette is ready. 
```
## Handling different kinds of files (Proof of principle)
###Load in data (ionic currents)
```{r}
file_list <- list(FI = "190903_0025.abf",
                  EPSP = "190903_0023.abf",
                  GJCC = "190903_0021.abf", 
                  GJVC = "190903_0020.abf",
                  
                  HTK  = "190903_0031.abf",
                  HTKC = "190903_0034.abf",
                  A    = "190903_0030.abf",
                  AC   = "190903_0033.abf")

trace_list <- map(seq_along(file_list), function(i){
  temp <- readABF_as_matrix2(path = paste0(abf_dir_path, 
                                           # "C:/Users/Daniel/Documents/Trace_Holding/", 
                                           file_list[[i]]),
                     channels = "all",
                     relative.time = T) %>%
    as.data.frame() %>% 
    janitor::clean_names(case = "upper_camel") %>% 
    mutate(Sweep = as.factor(Sweep)) %>% 
    group_by(Sweep) %>% 
    mutate(MinTime = min(Time, na.rm = T)) %>% 
    mutate(Time = Time - MinTime) %>% 
    select(-MinTime)
})

names(trace_list) <- names(file_list)
```

### Show all
```{r}
example_plots <- map(trace_list, function(i){
  downsample_data(i, len = 5000) %>%
    ungroup() %>% 
    gather(Ch, Value, c("In4","In7","In9","In12")) %>% 
    mutate(Cell = case_when(Ch %in% c("In4","In7") ~ "Cell A",
                            Ch %in% c("In9","In12") ~ "Cell B",)) %>% 
    mutate(ChType = case_when(Ch %in% c("In4","In9") ~ "mV",
                              Ch %in% c("In7","In12") ~ "nA",)) %>% 
    mutate(Ch = factor(.$Ch, levels = c("In4","In7","In9","In12"))) %>% 
    ggplot(aes(Time, Value, group = Sweep, color = Cell))+
    geom_line()+
    facet_wrap(ChType~Cell, scales = "free_y", ncol = 2)+
    labs(y = "")+
    theme(legend.position = "")+
    scale_color_aaas()
})

plot_grid(plotlist = example_plots)
```


###GJVC
```{r}
## GJVC: get Ig, Ileak====
temp <- trace_list$GJVC
### Setup



i_leak <- temp %>%
  filter(Time > 0.75) %>%
  mutate(In4 = as.numeric(In4)) %>%
  mutate(In7 = as.numeric(In7))

i_leak <- i_leak %>% 
  mutate(Segment = ifelse(Time >= 0.8 & Time <= 1.0, "PreStep", 
                          ifelse(Time >= 1.2 & Time <= 1.25, "Step", 
                                 "NA" ))) %>% 
  group_by(Sweep, Segment) %>% 
  mutate(In4Mean = mean(In4, na.rm = T),
         In7Mean = mean(In7, na.rm = T),
         In9Mean = mean(In9, na.rm = T),
         In12Mean = mean(In12, na.rm = T))

### Ig 
downsample_data(i_leak, len = 1000) %>% 
  gather("key", "value", c("In4", "In9")) %>% 
  ggplot(aes(Time, value, color = Segment, group = Sweep))+
  geom_path()+
  facet_grid(.~key)

i_g <- i_leak %>% 
  select(Sweep, Segment, In4Mean, 
         #In7Mean, 
         # In9Mean, 
         In12Mean
         ) %>% 
  filter(Segment != "NA") %>% 
  distinct() %>% 
  pivot_wider(names_from = "Segment", 
              values_from = c("In4Mean", "In12Mean")) %>% 
  mutate(In4Mean_Step = In4Mean_Step - In4Mean_PreStep,
         In12Mean_Step = In12Mean_Step - In12Mean_PreStep) %>% 
  select(Sweep, In4Mean_Step, In12Mean_Step) %>%
  rename(In4Mean = In4Mean_Step, In12Mean = In12Mean_Step) %>% 
  filter(abs(In4Mean) >= 4) 

i_g %>% 
  ggplot(aes(In4Mean, In12Mean))+
  geom_smooth(method = lm)+
  geom_point()

In4_to_In9_Ig <- as.numeric(broom::tidy(lm(In12Mean ~ In4Mean, data = i_g))[2, "estimate"])


### Ileak
i_leak %>% 
  ggplot(aes(Time, In4, color = Segment, group = Sweep))+
  geom_path()

i_leak <- i_leak %>% 
  ungroup() %>%
  select(Sweep, Segment, In4Mean, In7Mean) %>% 
  filter(Segment != "NA") %>% 
  distinct() %>% 
  filter(abs(In4Mean + 60) > 3 )
  
fm <- lm(In4Mean ~ In7Mean, data = i_leak)

In4_R <- as.numeric(broom::tidy(fm)[2, "estimate"])
```

###GJCC
```{r}
## GJCC: get CC, R_C, C, Rin ====
temp <- trace_list$GJCC

temp_plt <- temp %>% 
  filter(Sweep == 4) %>%
  mutate(In4 = as.numeric(In4)) %>% 
  mutate(In7 = as.numeric(In7))

# Show what the protocol looks like
plt1 <- downsample_data(temp_plt, len = 1000) %>% 
  gather(key, value, c("In4", "In9")) %>% 
  ggplot(aes(Time, value, color = key))+
  geom_path()

plt2 <- downsample_data(temp_plt, len = 1000) %>% 
  gather(key, value, c("In7", "In12")) %>% 
  mutate(key = factor(.$key, levels = c("In7", "In12"))) %>% 
  ggplot(aes(Time, value, color = key))+
  geom_path()

plt1/plt2

# annotate
temp <- temp %>% 
   mutate(Segment = case_when(Time >= 0       & Time <= 0.32820 ~ "A", #"PreStepIn12",
                              Time >= 1.32836 & Time <= 1.82836 ~ "B", #"StepIn12",
                              Time >= 2.57744 & Time <= 3.07744 ~ "C", #"PreStepIn7",
                              Time >= 4.07760 & Time <= 4.57760 ~ "D", #"StepIn7"
                              ))
```
$$r_{11}=\frac{v_1}{i_1}$$
$$r_{12}=\frac{v_2}{i_1}$$
$$r_1= \frac{r_{11}*r_{22} - r_{12}^2}{r_{22} - r_{12}}$$
$$r_c = \frac{r_{11}*r_{22} - r_{12}^2}{r_{12}}$$
```{r}
temp_resist <- temp %>% 
  group_by(Sweep, Segment) %>% 
  filter(!is.na(Segment)) %>% 
  summarise(MeanIn4 = mean(In4, na.rm = T),
            MeanIn7 = mean(In7, na.rm = T),
            MeanIn9 = mean(In9, na.rm = T),
            MeanIn12 = mean(In12, na.rm = T)) %>% 
  pivot_wider(names_from = Segment, values_from = c("MeanIn4", "MeanIn7", "MeanIn9", "MeanIn12")) %>% 
  mutate(In4_CC = MeanIn9_D/MeanIn4_D, #inj in In4
         In4_R11 = MeanIn4_D/MeanIn7_D,
         In4_R12 = MeanIn9_D/MeanIn7_D,

         
         In9_CC = MeanIn4_B/MeanIn9_B, #inj in In9
         In9_R11 = MeanIn9_B/MeanIn12_B,
         In9_R12 = MeanIn4_B/MeanIn12_B
         ) %>% 
  mutate(mean_R12 = (In4_R12+In9_R12)/2) %>% 
  mutate(In4_R1 = ((In4_R11*In9_R11) - (mean_R12^2)) / (In9_R11-mean_R12),
         In4_Rc = ((In4_R11*In9_R11) - (mean_R12^2)) / (mean_R12),
         
         In9_R1 = ((In9_R11*In4_R11) - (mean_R12^2)) / (In4_R11-mean_R12),
         In9_Rc = ((In9_R11*In4_R11) - (mean_R12^2)) / (mean_R12)
         ) %>% select(starts_with("In"))
```

```{r}
# V_rest
temp_rmp <- temp %>% 
  filter(Segment == "C") %>% 
  group_by(Sweep) %>% 
  summarise(In4_Vrest = min(In4, na.rm = T),
            In9_Vrest = min(In9, na.rm = T))
```


```{r}
# Tau
temp <- temp %>% 
   mutate(Segment = case_when(Time >= 3.07744 & Time <= 4.57760 ~ "In4Step", #"PreStepIn7",
                              Time >= 0.32820 & Time <= 1.82836 ~ "In9Step", #"StepIn7"
                              ))  

plt1 <- 
  downsample_data(temp, len = 1000) %>% 
  gather(Key, Value, c("In4", "In9")) %>% 
  ggplot(aes(Time, Value, color = Segment, group = interaction(Key, Sweep)))+
  geom_path()

plt2 <- 
  downsample_data(temp, len = 1000) %>% 
  ungroup() %>% 
  gather(key, value, c("In7", "In12")) %>% 
  mutate(key = factor(.$key, levels = c("In7", "In12"))) %>% 
  ggplot(aes(Time, value, color = Segment, group = interaction(key, Sweep)))+
  geom_path()

plt1/plt2

### test minpack.lm ####
# install.packages("minpack.lm")


temp_in9 <- temp %>% 
  filter(Segment == "In9Step") %>% 
  mutate(Time = Time - min(Time, na.rm = T))

test_fits <- map(unique(temp_in9$Sweep), function(i){
  fit_tau_1term_exp(df = filter(temp_in9, Sweep == i),
                    IV = "Time",
                    DV = "In9")  
})

test_fits_plts <- map(seq_along(test_fits), function(i){
  ggplot()+
    geom_line(data = as.data.frame(test_fits[[i]]$check_fit), aes(x = Time, y = Fit), color = "firebrick")+
    geom_line(data = as.data.frame(test_fits[[i]]$check_fit), aes(x = Time, y = In9), alpha = 0.8)+
    labs(subtitle = paste("tau =", as.character(
      round(test_fits[[i]]$fit[2, 2], digits = 3)
      )))
})

cowplot::plot_grid(plotlist = test_fits_plts)
```

###FI
```{r}
temp <- trace_list$FI

downsample_data(df = temp, len = 5000) %>% 
  gather(key, value, c("In9", "In12")) %>% 
  ungroup() %>% 
  mutate(key = factor(.$key, levels = c("In9", "In12"))) %>% 
  ggplot(aes(Time, value, group = Sweep))+
  geom_line()+
  facet_wrap(key~., scales = "free_y", ncol = 1)

#r11 == ~15.3
#r1 == ~17.9

place_params_for_predict_voltage_trace(tau = 19.9, 
                                       Rin = 15.3)

# place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == 10, ], 
#                                      Time.ch = "Time", 
#                                      Inj.ch = "In12")
# 
# run_predict_voltage_trace_py()
# 
# predicted_response <- retrieve_predicted_voltage()

predicted_response_list <- map(1:11, function(i){
  place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == i, ], 
                                       Time.ch = "Time", 
                                       Inj.ch = "In12")
  
  run_predict_voltage_trace_py()
  
  predicted_response <- retrieve_predicted_voltage()
  return(predicted_response)
})


my_plts <- map(
  seq_along(predicted_response_list),
  function(i){
    ggplot()+
      geom_line(data = predicted_response_list[[i]], aes(Time, predicted-56.5))+
      geom_line(data = temp[temp$Sweep == i, ], aes(Time, In9), color = "red")+
      labs(x = "Seconds", y = "mV")+
      coord_cartesian(y = c(-150, +120))
  })

# cowplot::plot_grid(plotlist = my_plts)


my_plts[[11]] / my_plts[[11 - 2]] / my_plts[[1 + 2]] / my_plts[[1]]
```

###EPSP
(epsp) How could we slice up the trace? 
```{r}
## Here's the stimulus used in the protocol ====
# sweep duration should be 19.687 seconds
epsp_stim <- readABF_as_matrix(here("inst", "extdata", "epsp_stim_files", "08 current injection.abf"),
                  channels = "Axo1I2")
epsp_stim <- as_tibble(epsp_stim) %>%
  mutate(Time = Time - min(Time, na.rm = T)) %>%
  rename(Stim = Axo1I2)


shading_annotations <- data.frame(
  starts = c(0.40,
             4.87,
             10.74,
             16.74),
  next_start = c(4.87,
                 10.74,
                 16.74,
                 19.685),
  equal_len = c(0.40,
                4.87,
                10.74,
                16.74) + 2.945,
  on_end = c(2,
             6.17,
             12.54, 
             18.5),
  equal_on = c(0.40,
               4.87,
               10.74,
               16.74) + 1.30
)

ggplot()+
  geom_vline(xintercept = c(shading_annotations$starts, shading_annotations$equal_len, shading_annotations$next_start, shading_annotations$equal_on), color = "gray")+
    geom_path(data = epsp_stim, aes(Time, Stim+1.5))+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = next_start, ymin = 0, ymax = 0.5), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[1], color = RColorBrewer::brewer.pal(3, "Set1")[1])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = equal_len, ymin = -0.5, ymax = 0), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[1], color = RColorBrewer::brewer.pal(3, "Set1")[1])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = on_end, ymin = -1, ymax = -0.5), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[2], color = RColorBrewer::brewer.pal(3, "Set1")[2])+
  geom_rect(data = shading_annotations, aes(xmin = starts, xmax = equal_on, ymin = -1.5, ymax = -1), alpha = 0.3, fill = RColorBrewer::brewer.pal(3, "Set1")[2], color = RColorBrewer::brewer.pal(3, "Set1")[2])+
  theme_classic()+
  geom_vline(xintercept = 12.54)+
  ylim(-1.5, 9.5)+
  labs(title = "Ways to Segement EPSP Stim")
```



```{r}
temp <- trace_list$EPSP

downsample_data(df = temp, len = 5000) %>% 
  gather(key, value, c("In9", "In12")) %>% 
  ungroup() %>% 
  mutate(key = factor(.$key, levels = c("In9", "In12"))) %>% 
  ggplot(aes(Time, value, group = Sweep))+
  geom_line()+
  facet_wrap(key~., scales = "free_y", ncol = 1)



#r11 == ~15.3
#r1 == ~17.9

place_params_for_predict_voltage_trace(tau = 19.9, 
                                       Rin = 15.3)

i=1
place_data_for_predict_voltage_trace(input.df = temp[temp$Sweep == i, ], 
                                       Time.ch = "Time", 
                                       Inj.ch = "In12")
  
run_predict_voltage_trace_py()
  
predicted_response <- retrieve_predicted_voltage()


ggplot()+
  geom_line(data = temp[temp$Sweep == i, ], aes(Time, In9), color = "red")+
  geom_line(data = predicted_response, aes(Time, predicted-68), color = "black")+
  labs(x = "Seconds", y = "mV")
      

  
```


#### Proof of principle: Contrasting simulaiton with LIF to regression and VIR
```{r}
M <- readABF_as_matrix2(path = 
                          paste0(abf_dir_path, "190915_0019.abf"),
                          # "C:/Users/Daniel/Documents/Trace_Holding/190915_0019.abf", #190924_0022.abf",
                   channels = "all",
                   relative.time = T)

temp <- as_tibble(M) %>% 
  janitor::clean_names(case = "upper_camel") %>% 
  mutate(Sweep = as.factor(Sweep)) %>% 
  group_by(Sweep) %>% 
  mutate(MinTime = min(Time, na.rm = T)) %>% 
  mutate(Time = Time - MinTime) %>% 
  filter(Sweep == 1) #%>% 
  # mutate(In7 = rollmean(In7, 17, fill = "extend"))


# temp %>% 
#   ggplot(aes(In7, In4))+
#   geom_path()+
#   geom_smooth(method = lm, fullrange = T, linetype = "dashed")+
#   theme_minimal()

fm <- lm(In4 ~ In7, data = temp)
fm_newdata <- data.frame(In4 = NA, 
                         In7 = temp$In7,
                         Time = temp$Time,
                         sweep = temp$Sweep)
fm_newdata$In4 <- predict(fm, newdata = fm_newdata)


temp <- temp[, c("Time", "In7", "In4")]

temp <- full_join(temp, rename(fm_newdata, lm = In4))

#TODO add in Rin / Tau programmatically

# 190915_0017 #-6nA
# 190915_0019 #epsp
# LC 5
# 
# Est. Rin: 51.21/6 = 8.535 MOhm
# Est. Taus: 
# Tau1			Tau2
# 58.482597351074219	11.020112037658691
# 21.417860031127930	N/A
place_params_for_predict_voltage_trace(tau = 21.417860031127930, Rin = 8.535)

place_data_for_predict_voltage_trace(input.df = temp, Time.ch = "Time", Inj.ch = "In7")

run_predict_voltage_trace_py()

predicted_response <- retrieve_predicted_voltage()



t1 <- temp
t2 <- as_tibble(predicted_response)

# # Feels hacky, but there seems to be a float rounding error here. E.g. Time 0.000199 != 0.0002
# t1$ms <- round(t1$Time * 10000)#/10000
# t2$ms <- round(t2$Time * 10000)#/10000
# 
# t1 <- t1 %>% dplyr::select(-Time)
# t2 <- t2 %>% dplyr::select(-Time)
# 
# t3 <- full_join(t1, t2) 

t3 <- cbind(t1, t2[, "predicted"]) 


t3$Vinf <- (t3$In7*8.535)-49.5
t3$predicted <- t3$predicted-49.5




plt_left <- 
t3 %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>% 
  ggplot(aes(Time, mV, color = Method))+
  geom_path()+
  geom_path(data = t3, aes(Time, In4), color = "black")+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)




t3_subtracted <- t3
t3_subtracted$lm <- t3_subtracted$In4 - t3_subtracted$lm
t3_subtracted$Vinf <- t3_subtracted$In4 - t3_subtracted$Vinf
t3_subtracted$predicted <- t3_subtracted$In4 - t3_subtracted$predicted
t3_subtracted$In4 <- t3_subtracted$In4 - -49.5

plt_mid <-
t3_subtracted %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>%
  ggplot(aes(Time, mV, color = Method))+
  geom_path()+ #TODO It seems there is a nA that's causing early termination here?
  geom_path(data = t3_subtracted, aes(Time, In4), color = "black")+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)

plt_right <- 
t3 %>% gather(key = "Method", value = "mV", c("lm", "Vinf", "predicted")) %>% 
  ggplot(aes(In4, mV, color = Method))+
  geom_path()+
  geom_abline(intercept = 0, slope = 1)+
  theme_minimal()+
  theme(legend.position = "")+
  facet_grid(Method~.)
  

(plt_left | plt_mid | plt_right) + plot_layout(widths = c(3, 3, 2))

```



## Check vs metadata

## 



#### </ end >
## Extend to batch processing
```{r}

#TODO
# works, now we need to automate the process. Maybe have a datasheet that we pull rin, tau from. 

to_use <- full_join(file_groups, files_df) %>% filter(Type == "epsp" & Group %in% c("Baseline", "compensated", "Delayed"))


ephys_meta <- readxl::read_excel(here("inst", "extdata", "ManualDataEphys02.xlsx"), sheet = "MetadataEphys") #"TECC", "TEVC", "IA", "IHTK"

ephys_meta <- ephys_meta %>% 
  mutate(num_zeros = 4 - floor(log(Recording))) %>% 
  mutate(num_zeros = ifelse(num_zeros == 3, "000", 
                            ifelse(num_zeros == 2, "00", 
                                   ifelse(num_zeros == 1, "0", NA)))) %>% 
  mutate(files = paste0(Experiment, "_", num_zeros, as.character(Recording), ".abf" ))


#


# trace_list <- map(seq(1, nrow(to_use)), function(i){
#   trace <- readABF_as_matrix(
#     path = paste0(traces_dir, "/", as.character(to_use[i, "files"])),
#     channels = c("IN 4", "IN 7", 
#                  "IN 9", "IN 12"#, "IN 14"
#     ))
#   
#   trace <- as.data.frame(trace) %>% 
#     janitor::clean_names(case = "upper_camel") %>% 
#     mutate(Time = Time - min(Time, na.rm = T),
#            Experiment = to_use[i, "Experiment"],
#            Group = to_use[i, "Group"],
#            files = to_use[i, "files"]
#     )
#   
#   if (ncol(trace) == 8){
#      return(trace) 
#   } else {
#     return(
#       data.frame(In4 = NA,
#                  In7 = NA, 
#                  In9 = NA, 
#                  In12 = NA, 
#                  Time = NA,
#                  Experiment = to_use[i, "Experiment"],
#                  Group = to_use[i, "Group"],
#                  files = to_use[i, "files"])
#       )
#   }
# })

# trace_df <- do.call(rbind, trace_list) %>% pivot_longer(names_to = "Channel", values_to = "mV", c("In4", "In7", "In9", "In12"))
# 
# 
# # find the low variance traces and drop them. Thesea are in the bath.
# trace_dstats <- trace_df %>%
#   group_by(files, Channel) %>%
#   summarise(sd = sd(mV, na.rm = T),
#             mean = mean(mV, na.rm = T),
#             min = min(mV, na.rm =T),
#             max = max(mV, na.rm = T)) %>%
#   mutate(range = abs(max - min))
# 
# trace_df <- full_join(trace_df, trace_dstats)
# 
# 
# trace_df$Channel <- factor(trace_df$Channel, levels = c("In4", "In9", "In7", "In12"))
# # GROUP = "Baseline"
# 
# 
# ## Big picture show everything ====
# for (GROUP  in c("Baseline", "Compensated", "Delayed")){
#   trace_df[seq(1, nrow(trace_df), by = 25), ] %>%
#     filter(Group == GROUP) %>%
#     mutate(colorvar = ifelse(Channel %in% c("In4", "In9"), "mV", "nA")) %>%
#     filter(colorvar == "mV") %>%
#     ggplot(aes(x = Time, y = mV, group = Channel, color = Channel))+
#     # scattermore::geom_scattermore()+
#     geom_path(alpha = 0.9)+
#     theme_minimal()+
#     theme(legend.position = "")+
#     scale_color_brewer(palette = "Set1")+
#     ylim(-70, -10)+
#     facet_wrap(.~files, scales = "free")
# 
#   ggsave(here("figures", paste0("prelim_trace_vis_", GROUP, ".pdf")), width = 9, height = 9)
# 
# }

```







# Working off of processed data ----
## Functions to move to ./R/ (2)
```{r}
## Shrug ====
shrug <- function(){cat("\\_()_/")}

## IV linear ====
iv_linear <- function(input.df = temp,
                             min.mV = -35,
                             max.mV = 5,
                             ch.i = "S2Max",
                             ch.v = "S1Max"){
  # input.df = temp
  # min.mV = -81
  # max.mV = -39
  # ch.i = "S2Max"
  # ch.v = "S1Max"
  
  input.df <- as.data.frame(input.df)
  
        # input.df <- input.df[!is.na(input.df[[ch.v]]), ]
  
  if (nrow(input.df[!is.na(input.df[[ch.v]]), ]) > 1 ){
      input.df <- input.df %>% rename(CH.I = ch.i) %>% rename(CH.V = ch.v)
  
  fm <- lm(CH.I ~ CH.V, input.df[input.df$CH.V >= min.mV & input.df$CH.V <= max.mV, ], na.action = "na.omit")
  
  }
  return(list(intercept = fm$coefficients[[1]],
       slope = fm$coefficients[[2]]))  

}

## mk_filename ====
# write file name from spreadsheet
mk_filename <- function(
  metadata.file = metadata,
  use.row = 1){
  filename <- paste0(
    as.character(
      metadata.file[use.row, "Experiment"]
    ),
    "_",
    paste0(
      rep("0", (4-length(metadata.file[use.row, "Recording"]))), collapse = ""),
    as.character(
      metadata.file[1, "Recording"]
    ),
    ".abf"
  )
  return(filename)
}


## Subtract leak from ihtk protocol
subtract_leak_df <- function(input.df = temp,
                             min.mV = -81,
                             max.mV = -39,
                             ch.i = "S2Max",
                             ch.v = "S1Max"){
  
  # input.df = temp
  # min.mV = -81
  # max.mV = -39
  # ch.i = "S2Max"
  # ch.v = "S1Max"
  
  input.df <- as.data.frame(input.df)
  
        # input.df <- input.df[!is.na(input.df[[ch.v]]), ]
  
  if (nrow(input.df[!is.na(input.df[[ch.v]]), ]) > 1 ){
      input.df <- input.df %>% rename(CH.I = ch.i) %>% rename(CH.V = ch.v)
  
  fm <- lm(CH.I ~ CH.V, input.df[input.df$CH.V >= min.mV & input.df$CH.V <= max.mV, ], na.action = "na.omit")
  
  input.df <- input.df %>% mutate(leak = predict(object = fm, newdata = input.df), na.action = "na.omit")
  input.df <- input.df %>% mutate(leak.sub = CH.I - leak)
  
  # input.df <- input.df %>% rename(ch.i = CH.I) %>% rename(ch.v = CH.V)
  
  names(input.df)[names(input.df) == "CH.I"] <- ch.i
  names(input.df)[names(input.df) == "CH.V"] <- ch.v
  
  
  # input.df %>% select(S1Max, S2Max, leak, leak.sub) %>% gather(type, value, 2:4) %>% ggplot(aes(x = S1Max, y = value, color = type))+geom_point()
  

  }
  return(input.df)  

}

```


See 01Merge*
## Load Data Ephys Data
```{r}
metadata <- read_excel(use.file.path,
                       sheet = "MetadataEphys")  

ia <- read_excel(
use.file.path,
  sheet = "IA"
)

ihtk <- read_excel(
use.file.path,
  sheet = "IHTK"
)

tecc <- read_excel(
use.file.path,
  sheet = "TECC"
)

tevc <- read_excel(
use.file.path,
  sheet = "TEVC"
)
```

# Voltage Clamp K+ Protocols
## IA data 
Add intercept/slope from -35 to 5mV
```{r}
# ia <- ia %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed") &
#                       Pharm %in% c("none", "tea"))

ia <- separate(ia, FileName, c("Experiment", "Recording"), sep = "_") %>% mutate(Recording = as.numeric(Recording))


ia <- right_join(x = 
  select(metadata, #Pharm, 
         Condition, #Notes, 
         In4,   In9, Experiment, Recording),
  y = ia)# %>% filter(Experiment != "0")

temp1 <- ia %>% select(-c(In9, S3Max, S4Max, S3Mean, S4Mean, Signal3, Signal4))
temp2 <- ia %>% select(-c(In4, S1Max, S2Max, S1Mean, S2Mean, Signal1, Signal2))

names(temp2) <- names(temp1)

ia <- full_join(temp1, temp2) %>% mutate(Cell = as.factor(In4))

# ia %>% 
#   # filter(Pharm != "4ap") %>% 
#   ggplot(aes(S1Max, S2Max, color = Cell))+
#   geom_point()+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()

ia$intercept <- NA %>% as.numeric() 
ia$slope <- NA %>% as.numeric()

ia <- ia %>% mutate(iter.var = paste(Experiment, Cell, Condition, sep =  "_"))
iter.over <- ia$iter.var %>% unique()

walk(1:length(iter.over), function(i){
  print(i)
  temp.df <- ia[ia$iter.var == iter.over[i], ]
  # temp <- select(temp, -c(leak, leak.sub))
  if(length(na.omit(temp.df$S2Max)) >1 &
     length(na.omit(temp.df$S1Max)) >1){
    
    temp.fm <- iv_linear(input.df = temp.df,
                         min.mV = -35,
                         max.mV = 5,
                         ch.i = "S2Max",
                         ch.v = "S1Max")
    if (length(temp.fm) > 0 ){
      ia[ia$iter.var == iter.over[i], "intercept"] <<- temp.fm$intercept
      ia[ia$iter.var == iter.over[i], "slope"] <<- temp.fm$slope    
    }}
})

# ia %>% 
#   ggplot(aes(Condition, intercept))+
#   geom_point()+
#   theme_minimal()
```

## IHTK data (not leak substracted)
```{r}
# ihtk <- ihtk %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed") &
#                       Pharm %in% c("none", "tea"))

ihtk <- separate(ihtk, FileName, c("Experiment", "Recording"), sep = "_") %>% mutate(Recording = as.numeric(Recording))


ihtk <- right_join(x = 
  select(metadata, #Pharm, 
         Condition, #Notes, 
         In4,   In9, Experiment, Recording),
  y = ihtk)# %>% filter(Experiment != "0")

temp1 <- ihtk %>% select(-c(In9, S3Max, S4Max, S3Mean, S4Mean, Signal3, Signal4))
temp2 <- ihtk %>% select(-c(In4, S1Max, S2Max, S1Mean, S2Mean, Signal1, Signal2))

names(temp2) <- names(temp1)

ihtk <- full_join(temp1, temp2) %>% mutate(In4 = as.factor(In4)) %>% rename(Cell = In4)

# ihtk %>% 
#   # filter(Pharm != "4ap") %>% 
#   ggplot(aes(S1Max, S2Max, color = Cell))+
#   geom_point()+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()
```

```{r}


ihtk <- ihtk %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed"))

ihtk <- ihtk[!is.na(ihtk[["Experiment"]]) & 
         !is.na(ihtk[["Cell"]]) &
         !is.na(ihtk[["Condition"]]), ] 

ihtk <- ihtk %>% 
  mutate(iter.var = paste(Experiment, Cell, Condition, sep =  "_")) %>% 
  mutate(leak = NA) %>% 
  mutate(leak.sub = NA)


iter.over <- ihtk$iter.var %>% unique()



# Add in leak subtracted measure
ihtk$na.action <- NA
walk(1:length(iter.over), function(i){
  print(i)
  temp <- ihtk[ihtk$iter.var == iter.over[i], ]
  temp <- select(temp, -c(leak, leak.sub))
  
  temp <- subtract_leak_df(input.df = temp,
                     min.mV = -81,
                     max.mV = -39,
                     ch.i = "S2Max",
                     ch.v = "S1Max")
  if(nrow(temp)>1){
    # make sure the columns are in the same order
    temp <- temp[, names(ihtk)]
    
    ihtk[ihtk$iter.var == iter.over[i], ] <<- temp      
  }
})

ihtk <- ihtk %>% mutate(leak = as.numeric(leak)) 
ihtk$leak.sub <- ihtk$S2Max - ihtk$leak


# ihtk %>% ggplot()+
#    geom_line(aes(x = S1Max, y = leak, color = Cell), linetype = "dashed")+
#    geom_point(aes(x = S1Max, y = leak.sub, color = Cell))+
#    geom_line(aes(x = S1Max, y = S2Max, color = Cell))+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()

# ggsave(plot = last_plot(), filename = "IonicExample.tiff", path = here("data", "figures"))

# ihtk %>% 
#   filter(Experiment == "190716") %>% 
#   ggplot()+
#    geom_line(aes(x = S1Max, y = leak, color = Cell), linetype = "dashed")+
#    geom_point(aes(x = S1Max, y = leak.sub, color = Cell))+
#    geom_line(aes(x = S1Max, y = S2Max, color = Cell))+
#   facet_grid(Condition ~ Cell)+
#   theme_bw()
```

Fit Roughly linear portion from IHTK
```{r}
ihtk$intercept <- NA %>% as.numeric() 
ihtk$slope <- NA %>% as.numeric()

walk(1:length(iter.over), function(i){
  print(i)
  temp.df <- ihtk[ihtk$iter.var == iter.over[i], ]
  # temp <- select(temp, -c(leak, leak.sub))
  if(nrow(temp.df) > 1){
    temp.fm <- iv_linear(input.df = temp.df,
                         min.mV = -35,
                         max.mV = 5,
                         ch.i = "S2Max",
                         ch.v = "S1Max")
    if (length(temp.fm) > 0 ){
      ihtk[ihtk$iter.var == iter.over[i], "intercept"] <<- temp.fm$intercept
      ihtk[ihtk$iter.var == iter.over[i], "slope"] <<- temp.fm$slope    
    }}
})


```

```{r}
# ihtk %>% 
#   ggplot(aes(Condition, intercept))+
#   geom_point()+
#   theme_minimal()
# 
# ihtk %>% 
#   ggplot(aes(Condition, slope))+
#   geom_point()+
#   theme_minimal()
```

## Join ephys into combined df
```{r}
temp1 <- ihtk %>% 
  select(#Pharm, 
         Condition, Cell, Experiment, intercept, slope) %>% 
  filter(!duplicated(.)) %>% 
  rename(Ihtk.0 = intercept) %>% 
  rename(Ihtk.Slope = slope)
temp2 <- ia %>% select(#Pharm, 
  Condition, Cell, Experiment, intercept, slope) %>% 
  filter(!duplicated(.)) %>% 
  rename(Ia.0 = intercept) %>% rename(Ia.Slope = slope)

ionic <- full_join(temp1, temp2) %>% 
  filter(Condition %in% c("Baseline", "Compensated", "Delayed")) %>% 
  mutate(Condition = factor(Condition, levels = c("Baseline", "Compensated", "Delayed")))
```

## Save ionic for later use
```{r}
save(ionic, file = here("data", "ionic.rds"))
```

# Voltage Clamp GJ Protocol
```{r}

ThresholdVoltage <- 4

# Keep only those with steps greater than threshold
ThresholdVector <- abs(tevc$R1S1Mean) >= ThresholdVoltage | abs(tevc$R1S3Mean) >= ThresholdVoltage 
tevc <- tevc[ThresholdVector, ]

# Look for the smallest deviation from baseline to find which cell is postsynaptic
# if TRUE then S1 is the presynaptic cell
tevc$S1Pre <- abs(tevc$R1S1Mean) >= abs(tevc$R1S3Mean)
tevc$PreSyn <- ifelse(tevc$S1Pre, tevc$Signal1, tevc$Signal3)

# Drop any rows where this wasn't a bool
tevc <- tevc[!is.na(tevc$S1Pre), ]

# conductance = i_post / delta_mV
# Where S1Pre == T
# c = R1S4Mean / R1S1Mean 
# Otherwise 
# c = R1S2Mean / R1S3Mean
temp <- tevc %>% 
  group_by(FileName, S1Pre) %>% 
  mutate(Ig = ifelse(S1Pre, 
                     abs(R1S4Mean / R1S1Mean), #abs to flip the current being used to prevent mV change into current coming across gj
                     abs(R1S2Mean / R1S3Mean) 
  )
  ) %>% 
  ungroup()

# provide Median observation
temp <- temp %>% 
  select(FileName, S1Pre, R1S1Mean, R1S2Mean, R1S3Mean, R1S4Mean, Ig) %>% 
  group_by(FileName, S1Pre) %>% 
  mutate(MedianIg = median(Ig, na.rm = T)) %>% 
  ungroup()

# Merge back
tevc <- full_join(tevc, temp)

save(tevc, file = here("data", "tevc.rds"))
```

# Current Clamp GJ Protocol
Bennet 1966's resistances:

Apparant Cell resistances:
$$r_{11}=\frac{v_1}{i_1}$$

Transfer resistances:
$$r_{12}=\frac{v_2}{i_1}$$

Membrane resistance
$$r_1= \frac{r_{11}*r_{22} - r_{12}^2}{r_{22} - r_{12}}$$

Coupling resistance
$$r_c = \frac{r_{11}*r_{22} - r_{12}^2}{r_{12}}$$

```{r}
ExperimentNames <- tecc$FileName %>% stringr::str_split(pattern = "_")
ExperimentNames <- transpose(ExperimentNames)[[1]] %>% unlist()

tecc$Experiment <- ExperimentNames
```


```{r}
df = tecc
v1 = "R1S1Mean"#"IN4_mean"
i1 = "R1S3Mean"#"IN7_mean"
v2 = "R1S4Mean"#"IN9_mean"
i2 = "R1S6Mean"#"IN12_mean"
exp = "Experiment"
rec = "FileName"

# Grouping prevents this from working.
df <- ungroup(df)

df <- df %>% mutate(cell = ifelse(abs(R1S3Mean) > abs(R1S6Mean), "a", "b"))

## Set up selection vectors for when i1 (e.g. IN7) is being used to inject current
inj_i1 <- abs(df[[i1]]) > abs(df[[i2]])
inj_i2 <- abs(df[[i1]]) < abs(df[[i2]])
## figure out coupling coef
df[inj_i1, "cc"] <- df[inj_i1, v2] / df[inj_i1, v1] #when inj IN7
df[inj_i2, "cc"] <- df[inj_i2, v1] / df[inj_i2, v2] #when inj IN12
## figure out input resistance ====
df[inj_i1, "r11"] <- df[inj_i1, v1] / df[inj_i1, i1] #when inj IN7
df[inj_i2, "r11"] <- df[inj_i2, v2] / df[inj_i2, i2] #when inj IN12
## figure out transfer resistance ====
df[inj_i1, "r12"] <- df[inj_i1, v2] / df[inj_i1, i1]
df[inj_i2, "r12"] <- df[inj_i2, v1] / df[inj_i2, i2]

## figure out membrane resist and coupling resist for both cells ====
temp <- df %>%
  dplyr::select(
    exp, rec, cell, r11, r12
  ) %>%
  group_by(Experiment, FileName, cell) %>% 
  # mutate(cell = ifelse(inj_i1, "cell1", "cell2")) %>%
  mutate(r11 = median(r11, na.rm = T),
         r12 = median(r12, na.rm = T)) %>% 
  distinct() %>% 
  ungroup() %>% 
  pivot_wider(names_from = cell,
              values_from = c("r11", "r12")
  ) %>%
  mutate(r1_a = ((r11_a*r11_b) - (r12_a^2)) / (r11_b - r12_a)) %>%
  mutate(r1_b = ((r11_b*r11_a) - (r12_b^2)) / (r11_a - r12_b)) %>%
  mutate(rc_a = ((r11_a*r11_b) - (r12_a^2)) / (r12_a)) %>%
  mutate(rc_b = ((r11_b*r11_a) - (r12_b^2)) / (r12_b)) %>%
  pivot_longer(
    -c(exp, rec),
    names_to = c(".value", "cell"),
    names_sep = "_",
    values_drop_na = TRUE
  )

# collapse df to medians
df <- df[, c(
  "Experiment", "cell", 
  "FileName", 
  # "Trace", "TraceStart", 
  "Signal1", "Signal2", "Signal3", "Signal4", "Signal5", "Signal6", 
  # "Region1", "StartTime", "EndTime", 
  "R1S1Mean", "R1S2Mean", "R1S3Mean", "R1S4Mean", "R1S5Mean", "R1S6Mean", 
  "R1S1Baseline", "R1S2Baseline", "R1S3Baseline", "R1S4Baseline", "R1S5Baseline", "R1S6Baseline", 
  # "FilePath", 
  "cc"#, 
  # "r11", "r12"
)] %>% 
  group_by(Experiment, cell, FileName) %>% 
  mutate(R1S1Mean = median(R1S1Mean, na.rm = T),
         R1S2Mean = median(R1S2Mean, na.rm = T),
         R1S3Mean = median(R1S3Mean, na.rm = T),
         R1S4Mean = median(R1S4Mean, na.rm = T),
         R1S5Mean = median(R1S5Mean, na.rm = T),
         R1S6Mean = median(R1S6Mean, na.rm = T),
         
         R1S1Baseline = median(R1S1Baseline, na.rm = T),
         R1S2Baseline = median(R1S2Baseline, na.rm = T),
         R1S3Baseline = median(R1S3Baseline, na.rm = T),
         R1S4Baseline = median(R1S4Baseline, na.rm = T),
         R1S5Baseline = median(R1S5Baseline, na.rm = T),
         R1S6Baseline = median(R1S6Baseline, na.rm = T),
         
         cc = median(cc, na.rm = T),
  ) %>% 
  distinct() %>% 
  ungroup()

# Merge
df <- full_join(df, temp) %>% dplyr::select(-cell)

tecc <- df
```

```{r}
save(tecc, file = here("data", "tecc.rds"))
```


# Molecular Data

## Read in Brian's Data
```{r}
# load all of brian's cells
BriansCells <- list.files(here("inst", "extdata", "BriansCells"))
BriansCells <- BriansCells[!(BriansCells == "All.CSV")]

BriansDfs <- map(BriansCells, function(i){
  temp <- read.csv(here("inst", "extdata", "BriansCells", i))
  names(temp) <- janitor::make_clean_names(names(temp), case = "upper_camel")
  temp$Condition <- i
  temp$Source <- "Brian"
  
  return(temp)
})

BriansDf <- do.call(rbind, BriansDfs)

BriansDf$Condition <- BriansDf$Condition %>% str_remove(pattern = ".CSV")

BriansDf$Time <- ifelse(str_detect(BriansDf$Condition, pattern = "Control") & !(str_detect(BriansDf$Condition, pattern = "24")), "Baseline",
                        ifelse(str_detect(BriansDf$Condition, pattern = "Acute"), "Compensated",
                               ifelse(str_detect(BriansDf$Condition, pattern = "24"), "Delayed", "NotFound")
                               )
                        )

BriansDf$Pharm <- ifelse(str_detect(BriansDf$Condition, pattern = "Control"), "None",
                        ifelse(str_detect(BriansDf$Condition, pattern = "TEA"), "TEA",
                               ifelse(str_detect(BriansDf$Condition, pattern = "AP"), "AP", 
                                      ifelse(str_detect(BriansDf$Condition, pattern = "TTX"), "TTX", "NotFound")
                                      )
                               )
                        )

BriansDf <- BriansDf[, names(BriansDf)[!(names(BriansDf) %in% c("Condition"))]]

BriansDf <- BriansDf %>% select(-Treatment)

BriansMetadataCols <- c("Source", "Pharm", "Time", "Cell")
BriansDf <- BriansDf[, c(BriansMetadataCols, names(BriansDf)[!(names(BriansDf) %in% BriansMetadataCols)]) ]


# df <- data.frame()
# walk(BriansCells, function(i){
#   df <<- rbind(df, read.csv(here("inst", "extdata", "BriansCells",i)))
# })
# 
# df <- df %>% mutate(Pharm = "") %>% mutate(Condition = "")
# 
# update.df.labels <- data.frame(stringsAsFactors=FALSE,
#                                Treatment = c("4AP24h", "Control", "24h-CONTROL", "TEA-24h", "TEA-Acute",
#                                              "TTX-24h"),
#                                Pharm = c("AP", "none", "none", "tea", "tea", "ttx"),
#                                Condition = c("Delayed", "Baseline", "Delayed", "Delayed", "Compensated",
#                                              "Delayed")
# )
# 
# walk(1:nrow(update.df.labels), function(i){
#   up.t <- update.df.labels[i, "Treatment"]
#   up.p <- update.df.labels[i, "Pharm"]
#   up.c <- update.df.labels[i, "Condition"]
#   
#   BriansDf[BriansDf$TREATMENT == up.t, "Pharm"] <<- up.p
#   BriansDf[BriansDf$TREATMENT == up.t, "Condition"] <<- up.c
# })
# 
# df <- df %>% rename(UID = CELL) %>% select(-TREATMENT)
# df <- as_tibble(df)
# # mutate(var = replace(var, var != "Candy", "Not Candy"))
```
## Read in data paired with ephys
```{r}
TEAOverTime <- readxl::read_excel(here("inst", "extdata", "LCTEAhr0hr1hr24.xlsx")) %>% janitor::clean_names(case = "upper_camel")

TEAOverTime$Time <- ifelse(TEAOverTime$Tea == 0, "Baseline", 
                           ifelse(TEAOverTime$Tea == 1, "Compensated", 
                                  ifelse(TEAOverTime$Tea == 24, "Delayed", "NotFound")))

TEAOverTime$Pharm <- "TEA"
TEAOverTime$Source <- "Daniel"

TEAOverTime <- TEAOverTime[, names(TEAOverTime)[!(names(TEAOverTime) %in% c("Tea"))]]

MetadataCols <- c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell")
TEAOverTime <- TEAOverTime[, c(MetadataCols, names(TEAOverTime)[!(names(TEAOverTime) %in% MetadataCols)]) ]
```

```{r}
# Make everything lower to ensure easy merging.
names(TEAOverTime)[!(names(TEAOverTime) %in% c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell"))] <- tolower(names(TEAOverTime)[!(names(TEAOverTime) %in% c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell"))])

names(BriansDf)[!(names(BriansDf) %in% c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell"))] <- tolower(names(BriansDf)[!(names(BriansDf) %in% c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell"))])






mrna <- full_join(TEAOverTime, BriansDf)
```

Rename gene names so they're consistent and easy to lookup with `./inst/extdata/mRNAInfo.xlsx`
```{r}
mRNAInfo <- readxl::read_excel(here("inst", "extdata", "mRNAInfo.xlsx")) # tables from Northcutt 2016 and annotations
ToCorrect <- names(mrna)[!(names(mrna) %in% c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell"))]
# ToCorrect <- tolower(ToCorrect)

# Get the names InData and the corresponding output names
SwapNames <- mRNAInfo[mRNAInfo$InDataLower %in% ToCorrect, c("InDataLower", "RGeneName")]
# SwapNames$InData <- tolower(SwapNames$InData)

for (i in 1:nrow(SwapNames)){
  ToCorrect[ToCorrect == as.character(SwapNames[i, "InDataLower"])] <- as.character(SwapNames[i, "RGeneName"])  
}

names(mrna) <- c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell", ToCorrect)
```


```{r}
save(mrna, file = here("data", "mrna.rds"))
```





#End
