---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(here)
library(tidyverse)
library(janitor)
# library("xlsx")
```

## User Defined Functions
```{r}
## Shrug ====
shrug <- function(){
  cat("¯\\_(ツ)_/¯")  }

## IV linear ====
iv_linear <- function(input.df = temp,
                             min.mV = -35,
                             max.mV = 5,
                             ch.i = "S2Max",
                             ch.v = "S1Max"){
  
  # input.df = temp
  # min.mV = -81
  # max.mV = -39
  # ch.i = "S2Max"
  # ch.v = "S1Max"
  
  input.df <- as.data.frame(input.df)
  
        # input.df <- input.df[!is.na(input.df[[ch.v]]), ]
  
  if (nrow(input.df[!is.na(input.df[[ch.v]]), ]) > 1 ){
      input.df <- input.df %>% rename(CH.I = ch.i) %>% rename(CH.V = ch.v)
  
  fm <- lm(CH.I ~ CH.V, input.df[input.df$CH.V >= min.mV & input.df$CH.V <= max.mV, ], na.action = "na.omit")
  
  }
  return(list(intercept = fm$coefficients[[1]],
       slope = fm$coefficients[[2]]))  

}

## mk_filename ====
# write file name from spreadsheet
mk_filename <- function(
  metadata.file = metadata,
  use.row = 1){
  filename <- paste0(
    as.character(
      metadata.file[use.row, "Experiment"]
    ),
    "_",
    paste0(
      rep("0", (4-length(metadata.file[use.row, "Recording"]))), collapse = ""),
    as.character(
      metadata.file[1, "Recording"]
    ),
    ".abf"
  )
  return(filename)
}
```

## Build metadata
```{r}
use.file.path <- here("inst", "extdata", "ManualDataEphys02.xlsx")
```

## Check entries in metadata file vs data files
```{r}

```

## Load Data Ephys Data
```{r}
metadata <- read_excel(use.file.path,
                       sheet = "MetadataEphys")  

ia <- read_excel(
use.file.path,
  sheet = "IA"
)

ihtk <- read_excel(
use.file.path,
  sheet = "IHTK"
)

tecc <- read_excel(
use.file.path,
  sheet = "TECC"
)

tevc <- read_excel(
use.file.path,
  sheet = "TEVC"
)
```

# Voltage Clamp K+ Protocols
## IA data 
Add intercept/slope from -35 to 5mV
```{r}
# ia <- ia %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed") &
#                       Pharm %in% c("none", "tea"))

ia <- separate(ia, FileName, c("Experiment", "Recording"), sep = "_") %>% mutate(Recording = as.numeric(Recording))


ia <- right_join(x = 
  select(metadata, #Pharm, 
         Condition, #Notes, 
         In4,   In9, Experiment, Recording),
  y = ia)# %>% filter(Experiment != "0")

temp1 <- ia %>% select(-c(In9, S3Max, S4Max, S3Mean, S4Mean, Signal3, Signal4))
temp2 <- ia %>% select(-c(In4, S1Max, S2Max, S1Mean, S2Mean, Signal1, Signal2))

names(temp2) <- names(temp1)

ia <- full_join(temp1, temp2) %>% mutate(Cell = as.factor(In4))

# ia %>% 
#   # filter(Pharm != "4ap") %>% 
#   ggplot(aes(S1Max, S2Max, color = Cell))+
#   geom_point()+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()

ia$intercept <- NA %>% as.numeric() 
ia$slope <- NA %>% as.numeric()

ia <- ia %>% mutate(iter.var = paste(Experiment, Cell, Condition, sep =  "_"))
iter.over <- ia$iter.var %>% unique()

walk(1:length(iter.over), function(i){
  print(i)
  temp.df <- ia[ia$iter.var == iter.over[i], ]
  # temp <- select(temp, -c(leak, leak.sub))
  if(length(na.omit(temp.df$S2Max)) >1 &
     length(na.omit(temp.df$S1Max)) >1){
    
    temp.fm <- iv_linear(input.df = temp.df,
                         min.mV = -35,
                         max.mV = 5,
                         ch.i = "S2Max",
                         ch.v = "S1Max")
    if (length(temp.fm) > 0 ){
      ia[ia$iter.var == iter.over[i], "intercept"] <<- temp.fm$intercept
      ia[ia$iter.var == iter.over[i], "slope"] <<- temp.fm$slope    
    }}
})

# ia %>% 
#   ggplot(aes(Condition, intercept))+
#   geom_point()+
#   theme_minimal()
```

## IHTK data (not leak substracted)
```{r}
# ihtk <- ihtk %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed") &
#                       Pharm %in% c("none", "tea"))

ihtk <- separate(ihtk, FileName, c("Experiment", "Recording"), sep = "_") %>% mutate(Recording = as.numeric(Recording))


ihtk <- right_join(x = 
  select(metadata, #Pharm, 
         Condition, #Notes, 
         In4,   In9, Experiment, Recording),
  y = ihtk)# %>% filter(Experiment != "0")

temp1 <- ihtk %>% select(-c(In9, S3Max, S4Max, S3Mean, S4Mean, Signal3, Signal4))
temp2 <- ihtk %>% select(-c(In4, S1Max, S2Max, S1Mean, S2Mean, Signal1, Signal2))

names(temp2) <- names(temp1)

ihtk <- full_join(temp1, temp2) %>% mutate(In4 = as.factor(In4)) %>% rename(Cell = In4)

# ihtk %>% 
#   # filter(Pharm != "4ap") %>% 
#   ggplot(aes(S1Max, S2Max, color = Cell))+
#   geom_point()+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()
```

```{r}
## Subtract leak from ihtk protocol
subtract_leak_df <- function(input.df = temp,
                             min.mV = -81,
                             max.mV = -39,
                             ch.i = "S2Max",
                             ch.v = "S1Max"){
  
  # input.df = temp
  # min.mV = -81
  # max.mV = -39
  # ch.i = "S2Max"
  # ch.v = "S1Max"
  
  input.df <- as.data.frame(input.df)
  
        # input.df <- input.df[!is.na(input.df[[ch.v]]), ]
  
  if (nrow(input.df[!is.na(input.df[[ch.v]]), ]) > 1 ){
      input.df <- input.df %>% rename(CH.I = ch.i) %>% rename(CH.V = ch.v)
  
  fm <- lm(CH.I ~ CH.V, input.df[input.df$CH.V >= min.mV & input.df$CH.V <= max.mV, ], na.action = "na.omit")
  
  input.df <- input.df %>% mutate(leak = predict(object = fm, newdata = input.df), na.action = "na.omit")
  input.df <- input.df %>% mutate(leak.sub = CH.I - leak)
  
  # input.df <- input.df %>% rename(ch.i = CH.I) %>% rename(ch.v = CH.V)
  
  names(input.df)[names(input.df) == "CH.I"] <- ch.i
  names(input.df)[names(input.df) == "CH.V"] <- ch.v
  
  
  # input.df %>% select(S1Max, S2Max, leak, leak.sub) %>% gather(type, value, 2:4) %>% ggplot(aes(x = S1Max, y = value, color = type))+geom_point()
  

  }
  return(input.df)  

}

ihtk <- ihtk %>% filter(Condition %in% c("Baseline", "Compensated", "Delayed"))

ihtk <- ihtk[!is.na(ihtk[["Experiment"]]) & 
         !is.na(ihtk[["Cell"]]) &
         !is.na(ihtk[["Condition"]]), ] 

ihtk <- ihtk %>% 
  mutate(iter.var = paste(Experiment, Cell, Condition, sep =  "_")) %>% 
  mutate(leak = NA) %>% 
  mutate(leak.sub = NA)


iter.over <- ihtk$iter.var %>% unique()



# Add in leak subtracted measure
ihtk$na.action <- NA
walk(1:length(iter.over), function(i){
  print(i)
  temp <- ihtk[ihtk$iter.var == iter.over[i], ]
  temp <- select(temp, -c(leak, leak.sub))
  
  temp <- subtract_leak_df(input.df = temp,
                     min.mV = -81,
                     max.mV = -39,
                     ch.i = "S2Max",
                     ch.v = "S1Max")
  if(nrow(temp)>1){
    # make sure the columns are in the same order
    temp <- temp[, names(ihtk)]
    
    ihtk[ihtk$iter.var == iter.over[i], ] <<- temp      
  }
})

ihtk <- ihtk %>% mutate(leak = as.numeric(leak)) 
ihtk$leak.sub <- ihtk$S2Max - ihtk$leak


# ihtk %>% ggplot()+
#    geom_line(aes(x = S1Max, y = leak, color = Cell), linetype = "dashed")+
#    geom_point(aes(x = S1Max, y = leak.sub, color = Cell))+
#    geom_line(aes(x = S1Max, y = S2Max, color = Cell))+
#   facet_grid(Condition ~ Experiment)+
#   theme_bw()

# ggsave(plot = last_plot(), filename = "IonicExample.tiff", path = here("data", "figures"))

# ihtk %>% 
#   filter(Experiment == "190716") %>% 
#   ggplot()+
#    geom_line(aes(x = S1Max, y = leak, color = Cell), linetype = "dashed")+
#    geom_point(aes(x = S1Max, y = leak.sub, color = Cell))+
#    geom_line(aes(x = S1Max, y = S2Max, color = Cell))+
#   facet_grid(Condition ~ Cell)+
#   theme_bw()
```

Fit Roughly linear portion from IHTK
```{r}
ihtk$intercept <- NA %>% as.numeric() 
ihtk$slope <- NA %>% as.numeric()

walk(1:length(iter.over), function(i){
  print(i)
  temp.df <- ihtk[ihtk$iter.var == iter.over[i], ]
  # temp <- select(temp, -c(leak, leak.sub))
  if(nrow(temp.df) > 1){
    temp.fm <- iv_linear(input.df = temp.df,
                         min.mV = -35,
                         max.mV = 5,
                         ch.i = "S2Max",
                         ch.v = "S1Max")
    if (length(temp.fm) > 0 ){
      ihtk[ihtk$iter.var == iter.over[i], "intercept"] <<- temp.fm$intercept
      ihtk[ihtk$iter.var == iter.over[i], "slope"] <<- temp.fm$slope    
    }}
})


```

```{r}
# ihtk %>% 
#   ggplot(aes(Condition, intercept))+
#   geom_point()+
#   theme_minimal()
# 
# ihtk %>% 
#   ggplot(aes(Condition, slope))+
#   geom_point()+
#   theme_minimal()
```

## Join ephys into combined df
```{r}
temp1 <- ihtk %>% 
  select(#Pharm, 
         Condition, Cell, Experiment, intercept, slope) %>% 
  filter(!duplicated(.)) %>% 
  rename(Ihtk.0 = intercept) %>% 
  rename(Ihtk.Slope = slope)
temp2 <- ia %>% select(#Pharm, 
  Condition, Cell, Experiment, intercept, slope) %>% 
  filter(!duplicated(.)) %>% 
  rename(Ia.0 = intercept) %>% rename(Ia.Slope = slope)

ionic <- full_join(temp1, temp2) %>% 
  filter(Condition %in% c("Baseline", "Compensated", "Delayed")) %>% 
  mutate(Condition = factor(Condition, levels = c("Baseline", "Compensated", "Delayed")))
```

## Save ionic for later use
```{r}
save(ionic, file = here("data", "ionic.rds"))
```

# Voltage Clamp GJ Protocol
```{r}

ThresholdVoltage <- 4

# Keep only those with steps greater than threshold
ThresholdVector <- abs(tevc$R1S1Mean) >= ThresholdVoltage | abs(tevc$R1S3Mean) >= ThresholdVoltage 
tevc <- tevc[ThresholdVector, ]

# Look for the smallest deviation from baseline to find which cell is postsynaptic
# if TRUE then S1 is the presynaptic cell
tevc$S1Pre <- abs(tevc$R1S1Mean) >= abs(tevc$R1S3Mean)
tevc$PreSyn <- ifelse(tevc$S1Pre, tevc$Signal1, tevc$Signal3)

# Drop any rows where this wasn't a bool
tevc <- tevc[!is.na(tevc$S1Pre), ]

# conductance = i_post / delta_mV
# Where S1Pre == T
# c = R1S4Mean / R1S1Mean 
# Otherwise 
# c = R1S2Mean / R1S3Mean
temp <- tevc %>% 
  group_by(FileName, S1Pre) %>% 
  mutate(Ig = ifelse(S1Pre, 
                     abs(R1S4Mean / R1S1Mean), #abs to flip the current being used to prevent mV change into current coming across gj
                     abs(R1S2Mean / R1S3Mean) 
  )
  ) %>% 
  ungroup()

# provide Median observation
temp <- temp %>% 
  select(FileName, S1Pre, R1S1Mean, R1S2Mean, R1S3Mean, R1S4Mean, Ig) %>% 
  group_by(FileName, S1Pre) %>% 
  mutate(MedianIg = median(Ig, na.rm = T)) %>% 
  ungroup()

# Merge back
tevc <- full_join(tevc, temp)

save(tevc, file = here("data", "tevc.rds"))
```

# Current Clamp GJ Protocol
Bennet 1966's resistances:

Apparant Cell resistances:
$$r_{11}=\frac{v_1}{i_1}$$

Transfer resistances:
$$r_{12}=\frac{v_2}{i_1}$$

Membrane resistance
$$r_1= \frac{r_{11}*r_{22} - r_{12}^2}{r_{22} - r_{12}}$$

Coupling resistance
$$r_c = \frac{r_{11}*r_{22} - r_{12}^2}{r_{12}}$$

```{r}
ExperimentNames <- tecc$FileName %>% stringr::str_split(pattern = "_")
ExperimentNames <- transpose(ExperimentNames)[[1]] %>% unlist()

tecc$Experiment <- ExperimentNames
```


```{r}
df = tecc
v1 = "R1S1Mean"#"IN4_mean"
i1 = "R1S3Mean"#"IN7_mean"
v2 = "R1S4Mean"#"IN9_mean"
i2 = "R1S6Mean"#"IN12_mean"
exp = "Experiment"
rec = "FileName"

# Grouping prevents this from working.
df <- ungroup(df)

df <- df %>% mutate(cell = ifelse(abs(R1S3Mean) > abs(R1S6Mean), "a", "b"))

## Set up selection vectors for when i1 (e.g. IN7) is being used to inject current
inj_i1 <- abs(df[[i1]]) > abs(df[[i2]])
inj_i2 <- abs(df[[i1]]) < abs(df[[i2]])
## figure out coupling coef
df[inj_i1, "cc"] <- df[inj_i1, v2] / df[inj_i1, v1] #when inj IN7
df[inj_i2, "cc"] <- df[inj_i2, v1] / df[inj_i2, v2] #when inj IN12
## figure out input resistance ====
df[inj_i1, "r11"] <- df[inj_i1, v1] / df[inj_i1, i1] #when inj IN7
df[inj_i2, "r11"] <- df[inj_i2, v2] / df[inj_i2, i2] #when inj IN12
## figure out transfer resistance ====
df[inj_i1, "r12"] <- df[inj_i1, v2] / df[inj_i1, i1]
df[inj_i2, "r12"] <- df[inj_i2, v1] / df[inj_i2, i2]

## figure out membrane resist and coupling resist for both cells ====
temp <- df %>%
  dplyr::select(
    exp, rec, cell, r11, r12
  ) %>%
  group_by(Experiment, FileName, cell) %>% 
  # mutate(cell = ifelse(inj_i1, "cell1", "cell2")) %>%
  mutate(r11 = median(r11, na.rm = T),
         r12 = median(r12, na.rm = T)) %>% 
  distinct() %>% 
  ungroup() %>% 
  pivot_wider(names_from = cell,
              values_from = c("r11", "r12")
  ) %>%
  mutate(r1_a = ((r11_a*r11_b) - (r12_a^2)) / (r11_b - r12_a)) %>%
  mutate(r1_b = ((r11_b*r11_a) - (r12_b^2)) / (r11_a - r12_b)) %>%
  mutate(rc_a = ((r11_a*r11_b) - (r12_a^2)) / (r12_a)) %>%
  mutate(rc_b = ((r11_b*r11_a) - (r12_b^2)) / (r12_b)) %>%
  pivot_longer(
    -c(exp, rec),
    names_to = c(".value", "cell"),
    names_sep = "_",
    values_drop_na = TRUE
  )

# collapse df to medians
df <- df[, c(
  "Experiment", "cell", 
  "FileName", 
  # "Trace", "TraceStart", 
  "Signal1", "Signal2", "Signal3", "Signal4", "Signal5", "Signal6", 
  # "Region1", "StartTime", "EndTime", 
  "R1S1Mean", "R1S2Mean", "R1S3Mean", "R1S4Mean", "R1S5Mean", "R1S6Mean", 
  "R1S1Baseline", "R1S2Baseline", "R1S3Baseline", "R1S4Baseline", "R1S5Baseline", "R1S6Baseline", 
  # "FilePath", 
  "cc"#, 
  # "r11", "r12"
)] %>% 
  group_by(Experiment, cell, FileName) %>% 
  mutate(R1S1Mean = median(R1S1Mean, na.rm = T),
         R1S2Mean = median(R1S2Mean, na.rm = T),
         R1S3Mean = median(R1S3Mean, na.rm = T),
         R1S4Mean = median(R1S4Mean, na.rm = T),
         R1S5Mean = median(R1S5Mean, na.rm = T),
         R1S6Mean = median(R1S6Mean, na.rm = T),
         
         R1S1Baseline = median(R1S1Baseline, na.rm = T),
         R1S2Baseline = median(R1S2Baseline, na.rm = T),
         R1S3Baseline = median(R1S3Baseline, na.rm = T),
         R1S4Baseline = median(R1S4Baseline, na.rm = T),
         R1S5Baseline = median(R1S5Baseline, na.rm = T),
         R1S6Baseline = median(R1S6Baseline, na.rm = T),
         
         cc = median(cc, na.rm = T),
  ) %>% 
  distinct() %>% 
  ungroup()

# Merge
df <- full_join(df, temp) %>% dplyr::select(-cell)

tecc <- df
```

```{r}
save(tecc, file = here("data", "tecc.rds"))
```


# Molecular Data

## Read in Brian's Data
```{r}
# load all of brian's cells
BriansCells <- list.files(here("inst", "extdata", "BriansCells"))
BriansCells <- BriansCells[!(BriansCells == "All.CSV")]

BriansDfs <- map(BriansCells, function(i){
  temp <- read.csv(here("inst", "extdata", "BriansCells", i))
  names(temp) <- janitor::make_clean_names(names(temp), case = "upper_camel")
  temp$Condition <- i
  temp$Source <- "Brian"
  
  return(temp)
})

BriansDf <- do.call(rbind, BriansDfs)

BriansDf$Condition <- BriansDf$Condition %>% str_remove(pattern = ".CSV")

BriansDf$Time <- ifelse(str_detect(BriansDf$Condition, pattern = "Control") & !(str_detect(BriansDf$Condition, pattern = "24")), "Baseline",
                        ifelse(str_detect(BriansDf$Condition, pattern = "Acute"), "Compensated",
                               ifelse(str_detect(BriansDf$Condition, pattern = "24"), "Delayed", "NotFound")
                               )
                        )

BriansDf$Pharm <- ifelse(str_detect(BriansDf$Condition, pattern = "Control"), "None",
                        ifelse(str_detect(BriansDf$Condition, pattern = "TEA"), "TEA",
                               ifelse(str_detect(BriansDf$Condition, pattern = "AP"), "AP", 
                                      ifelse(str_detect(BriansDf$Condition, pattern = "TTX"), "TTX", "NotFound")
                                      )
                               )
                        )

BriansDf <- BriansDf[, names(BriansDf)[!(names(BriansDf) %in% c("Condition"))]]

BriansDf <- BriansDf %>% select(-Treatment)

BriansMetadataCols <- c("Source", "Pharm", "Time", "Cell")
BriansDf <- BriansDf[, c(BriansMetadataCols, names(BriansDf)[!(names(BriansDf) %in% BriansMetadataCols)]) ]


# df <- data.frame()
# walk(BriansCells, function(i){
#   df <<- rbind(df, read.csv(here("inst", "extdata", "BriansCells",i)))
# })
# 
# df <- df %>% mutate(Pharm = "") %>% mutate(Condition = "")
# 
# update.df.labels <- data.frame(stringsAsFactors=FALSE,
#                                Treatment = c("4AP24h", "Control", "24h-CONTROL", "TEA-24h", "TEA-Acute",
#                                              "TTX-24h"),
#                                Pharm = c("AP", "none", "none", "tea", "tea", "ttx"),
#                                Condition = c("Delayed", "Baseline", "Delayed", "Delayed", "Compensated",
#                                              "Delayed")
# )
# 
# walk(1:nrow(update.df.labels), function(i){
#   up.t <- update.df.labels[i, "Treatment"]
#   up.p <- update.df.labels[i, "Pharm"]
#   up.c <- update.df.labels[i, "Condition"]
#   
#   BriansDf[BriansDf$TREATMENT == up.t, "Pharm"] <<- up.p
#   BriansDf[BriansDf$TREATMENT == up.t, "Condition"] <<- up.c
# })
# 
# df <- df %>% rename(UID = CELL) %>% select(-TREATMENT)
# df <- as_tibble(df)
# # mutate(var = replace(var, var != "Candy", "Not Candy"))
```
## Read in data paired with ephys
```{r}
TEAOverTime <- readxl::read_excel(here("inst", "extdata", "LCTEAhr0hr1hr24.xlsx")) %>% janitor::clean_names(case = "upper_camel")

TEAOverTime$Time <- ifelse(TEAOverTime$Tea == 0, "Baseline", 
                           ifelse(TEAOverTime$Tea == 1, "Compensated", 
                                  ifelse(TEAOverTime$Tea == 24, "Delayed", "NotFound")))

TEAOverTime$Pharm <- "TEA"
TEAOverTime$Source <- "Daniel"

TEAOverTime <- TEAOverTime[, names(TEAOverTime)[!(names(TEAOverTime) %in% c("Tea"))]]

MetadataCols <- c("Source", "Pharm", "Time", "Sample", "Experiment", "Cell")
TEAOverTime <- TEAOverTime[, c(MetadataCols, names(TEAOverTime)[!(names(TEAOverTime) %in% MetadataCols)]) ]
```

```{r}
mrna <- full_join(TEAOverTime, BriansDf)
```


```{r}
save(mrna, file = here("data", "mrna.rds"))
```





#End

## Overview of the data

| thing | File Name | Description |
| a | LCTEAhr0hr1hr24.xlsx | Contains mRNA data to accompany the ephys data I collected. |
| b | LCTEAhr0hr1hr24.xlsx | Contains mRNA data to accompany the ephys data I collected. |
| c | LCTEAhr0hr1hr24.xlsx | Contains mRNA data to accompany the ephys data I collected. |

## Read in data


# Not run
## from untitled2.
```{r eval=FALSE, include=FALSE}
non.metadata <- c("TECC", "TEVC", "IA", "IHTK")
metadata <- c("MetadataEphys")

use.file.path <- here("inst", "extdata", "ManualDataEphys02.xlsx")

# Read in manual metadata for comparsions
man.metadata <- read_excel(use.file.path, 
                           sheet = metadata)  

# Read in data
M <- purrr::map(non.metadata, function(i){
read_excel(use.file.path, 
           sheet = i)  
}) 
names(M) <- non.metadata

# Remove the relevant portions, i.e. the filenames and sheet names
M <- map(1:length(M), function(i){
  temp <- M[[i]] %>% select(FileName) %>% unique()
  temp <- temp %>% mutate(Type = as.character(names(M)[i]))
  return(temp)
})

# Combine into a single df
made.metadata <- data.frame()
walk(M, function(i){
  made.metadata <<- rbind(made.metadata, i)
})

# Massage to make it look like the manual metadata
made.metadata <- made.metadata %>% 
  mutate(FileName = str_remove(made.metadata$FileName, ".abf")) %>% 
  separate(., FileName, c("Experiment", "Recording"), sep = "_") %>% 
  mutate(Recording = as.numeric(Recording))

made.metadata$Data <- T
man.metadata$MData <- T

man.metadata <- man.metadata %>% rename(type = Type)

all.metadata <- left_join(made.metadata, man.metadata)

all.metadata <- all.metadata %>% arrange(Experiment, Recording)

# Interpolate metadata

# install.packages("xlsx")
library("xlsx")

# xlsx::write.xlsx(made.metadata, 
#                  file = "S:/Data_Daniel/ActiveProjects/mRNA24hLC/inst/extdata/ManualDataEphys.xlsx",
#                  sheetName = "MadeMetadata", 
#                  append = T)

xlsx::write.xlsx(all.metadata, 
                 file = use.file.path,
                 sheetName = "AllMetadata", 
                 append = T)
```
### Mol Bio
```{r eval=FALSE, include=FALSE}
M.none.B <- as.data.frame(read.csv("inst/extdata/Control.csv"))
M.tea.C <- as.data.frame(read.csv("inst/extdata/TEAAcute.CSV"))
M.tea.D <- as.data.frame(read.csv("inst/extdata/TEA24hr.CSV"))

M.none.B <- M.none.B %>% 
  rename(UID = CELL) %>% 
  mutate(Pharm = "none") %>% 
  mutate(Condition = "Baseline") %>% 
  select(-TREATMENT)

M.tea.C <- M.tea.C %>% 
  rename(UID = CELL) %>% 
  mutate(Pharm = "tea") %>% 
  mutate(Condition = "Compensated") %>% 
  select(-TREATMENT)

M.tea.D <- M.tea.D %>% 
  rename(UID = CELL) %>% 
  mutate(Pharm = "tea") %>% 
  mutate(Condition = "Delayed") %>% 
  select(-TREATMENT)

mrna <- full_join(M.none.B, M.tea.C) %>% full_join(., M.tea.D)

mrna.names <- mrna %>% select(-c(UID, Pharm, Condition)) %>% names()
mrna.names <- mrna.names[mrna.names %in% c("BKKCa", "SHAL", "Shaker")]

#, "Shab", "Shaw1", "Shaw2")]

cowplot::plot_grid(plotlist = 
map(mrna.names, function(i){
    ggplot(mrna, aes(x = Condition, group = Condition, fill = Condition))+
  # geom_smooth(method = "lm", se = F)+
    geom_boxplot(aes_string(y = i), width = 0.1)+
    ggbeeswarm::geom_beeswarm(aes_string(y = i), shape = 1)+
    # geom_point(size = 2)+
    stat_summary(aes_string(y = i, group = "1"), fun.y = mean, geom = "line")+
    stat_summary(aes_string(y = i, group = "1"), fun.y = mean, geom = "point", size = 4, shape = 4)+
    theme_minimal()+
  theme(legend.position = "")+
  labs(x = "", y = "", title = i)
}), ncol = 3
)

ggsave(plot = last_plot(), filename = "kchannels.tiff", path = here("data", "figures"))
# cowplot::plot_grid(plotlist = map(c("BKKCa", "Shaker", "Shab", "Shaw1", "Shaw2"), function(i){
#   ggplot(mrna, aes_string("CONDITION", i))+
#     geom_violin()+
#     geom_point()+
#     stat_summary(fun.y = "mean", geom = "point", size = 3, color = "red", shape = 15)+
#     theme_minimal()
# })
# )






```
### Find what data is missing from each sheet
```{r eval=FALSE, include=FALSE}
ihtk <- ihtk %>% mutate(FileName = paste0(FileName, ".abf"))
ia <- ia %>% mutate(FileName = paste0(FileName, ".abf"))




# Add FileName to help merge
metadata$FileName <- NA
walk(1:nrow(metadata), function(i){
  metadata[i, "FileName"] <<- mk_filename(
  metadata.file = metadata,
  use.row = i)
})







find_missing_entries <- function(
  data.file = ihtk,
  sheet = "ihtk",
  metadata.file = metadata,
  error.path = "inst/extdata"
){
  # find those that are not in metadata
  uniq.d <- unique(data.file$FileName)
  uniq.m <- unique(metadata.file$FileName)
  
  # the following metadata is not represented in the data
  m.i.d <- data.frame("MissingInData" = uniq.m[!(uniq.m %in% uniq.d)] )
  
  if (nrow(m.i.d) > 0){
    warning("Metadata entries found that were not in the data file.")
    warning(paste0("Writing error file at ", as.character(here(error.path, "MissingInMetadata.csv"))))
    m.i.d <- m.i.d %>% separate(., MissingInData, c("Experiment", "Recording"), sep = "_")
    m.i.d$Recording <- m.i.d$Recording %>% str_remove(".abf") %>% as.numeric()
    m.i.d$Type <- sheet
    if(!file.exists(here(error.path, "MissingInData.csv"))){
      
    }else if (file.exists(here(error.path, "MissingInData.csv"))){
      old.m.i.d <- read.csv(here(error.path, "MissingInData.csv"))
      m.i.d <- rbind(old.m.i.d[,-1], m.i.d) # need to drop the rownum col
    }
    write.csv(m.i.d, here(error.path, "MissingInData.csv"))
  }
  
  # the following data is not represented in the metadata
  m.i.m <- data.frame("MissingInMetadata" = uniq.d[!(uniq.d %in% uniq.m)] )
  
  if (nrow(m.i.m) > 0){
    warning("Data entries found that were not in metadata.")
    warning(paste0("Writing error file at ", as.character(here(error.path, "MissingInMetadata.csv"))))
    m.i.m <- m.i.m %>% separate(., MissingInMetadata, c("Experiment", "Recording"), sep = "_")
    m.i.m$Recording <- m.i.m$Recording %>% str_remove(".abf") %>% as.numeric()
    m.i.m$Type <- sheet
    
    if(!file.exists(here(error.path, "MissingInMetadata.csv"))){
      
    }else if (file.exists(here(error.path, "MissingInMetadata.csv"))){
      old.m.i.m <- read.csv(here(error.path, "MissingInMetadata.csv"))
      m.i.m <- rbind(old.m.i.m[, -1], m.i.m)# need to drop the rownum col
    }
    write.csv(m.i.m, here(error.path, "MissingInMetadata.csv"))
    
    # update.in.r <- readline(prompt="Update metadata in R? Y/N: ")
    # while (!(update.in.r %in% c("Y", "y", "N", "n"))){
    #   update.in.r <- readline(prompt="Update metadata in R? Y/N: ")
    # }
    # # interactive update
    # if (update.in.r %in% c("Y", "y")){
    #   print("Updating in r is a planned but not present feature. Please fork the repository or contact the package maintainer.")
    #   # m.i.m %>% mutate()
    #   # 
    #   # cbind(m.i.m, 
    #   # metadata.file[0, ]
    #   # )
    #   
    #   # let user enter each desired value
    #   # return metadata. Writing into xlsx will be more hastle than it's worth
    #   # Not focusing on this now, it'll be easier for me ATM to do this updating in excel.
    # }
    # no update
  }
  
}

find_missing_entries(
  data.file = ihtk,
  sheet = "IHTK",
  metadata.file = metadata,
  error.path = "inst/extdata"
)

find_missing_entries(
  data.file = ia,
  sheet = "IA",
  metadata.file = metadata,
  error.path = "inst/extdata"
)

find_missing_entries(
  data.file = tecc,
  sheet = "TECC",
  metadata.file = metadata,
  error.path = "inst/extdata"
)

find_missing_entries(
  data.file = tevc,
  sheet = "TEVC",
  metadata.file = metadata,
  error.path = "inst/extdata"
)


#idk why but this seems to not be joining them.










```











