---
title: "Shelved IHTK IA Code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Newer
###HTK/A
```{r}
## I_x: get I_x linear intercept, I_x slope, Ileak====

### IHTK
# 1. plot to get user to say which to drop (if there is no file with this info) # done
# 2. smooth # done
# 3. get peak values # done
# 4. get sustained values
# 5. subtract off leak # done
# 6. report values and leak # done
temp <- trace_list$HTK

smooth_k = 15 #7
peak_start = 0.27
peak_end = 0.29

end_start = 0.7
end_end = 0.75

# smooth
temp <- temp %>% 
  group_by(Sweep) %>% 
  mutate(across(names(temp)[!(names(temp)%in%c("Sweep", "Time"))], ~ zoo::rollmean(.x, k = smooth_k, fill = NA))) %>% #as.character(.x))) 
  ungroup()


temp %>% 
  ggplot(aes(x = Time, y = In7))+
  geom_line(aes(color = Sweep))+
  geom_vline(xintercept = c(peak_start, peak_end))+
  geom_vline(xintercept = c(end_start, end_end))+
  # geom_rect(aes(xmin = 0.27, 
  #           xmax = 0.29, 
  #           ymin = -11,
  #           ymax = 25), alpha = 0.03
  #           # data = data.frame(Time = c(0.27, 0.29),
  #           #                               In7 = c(-11, 25))
  # )+
  coord_cartesian(y = c(-11, 25))#, x = c(0.2, 0.4))



# What do the estimates look like? If there's skew we should consider using a percentile instead of a mean.
plt1 <- temp %>% 
  group_by(Sweep) %>% 
  filter(Time > peak_start & Time < peak_end) %>% 
  ggplot(aes(x = In7, group = Sweep, color = Sweep))+geom_density()+coord_cartesian(x = c(-7, 20))+theme(legend.position = "")+labs(title = "Transient Portion")

plt2 <- temp %>% 
  group_by(Sweep) %>% 
  filter(Time > end_start & Time < end_end) %>%
  ggplot(aes(x = In7, group = Sweep, color = Sweep))+geom_density()+coord_cartesian(x = c(-7, 20))+theme(legend.position = "")+labs(title = "Sustained Portion")

plt1/plt2
# For the transients we'll use the max or a high percentile.
# Sustained looks much safer to use the mean (as expected) but there's inequal spread, presumably where we have activity or artifacts.


## calculating leak

temp_end <- temp %>% 
  filter(Time > end_start & Time < end_end) %>%
  group_by(Sweep) %>% 
  summarise(In4_q90  = quantile(In4,  prob = c(0.9)),
            In7_q90  = quantile(In7,  prob = c(0.9)),
            In9_q90  = quantile(In9,  prob = c(0.9)),
            In12_q90 = quantile(In12, prob = c(0.9)) )

temp_end %>% 
  ggplot(aes(x = Sweep, y = In7_q90, group = 1))+geom_point()+geom_smooth(method = "lm")




passive_region_min <- -85
passive_region_max <- -38

leak_fm1 <- lm(In7_q90  ~ In4_q90, temp_end[temp_end$In4_q90 > passive_region_min & temp_end$In4_q90 < passive_region_max, c("In4_q90", "In7_q90")])
leak_fm2 <- lm(In12_q90 ~ In9_q90, temp_end[temp_end$In9_q90 > passive_region_min & temp_end$In9_q90 < passive_region_max, c("In9_q90", "In12_q90")])

temp_end <- temp_end %>% 
  mutate(
  In7_q90_leak  = predict(object = leak_fm1, newdata = temp_end),
  In12_q90_leak = predict(object = leak_fm2, newdata = temp_end)
) %>% mutate(
  In7_q90_ls  = In7_q90 - In7_q90_leak,
  In12_q90_ls = In12_q90 - In12_q90_leak
)




temp_end %>% 
  gather(key = "key", value = "nA", c("In7_q90", "In7_q90_leak", "In7_q90_ls")) %>% 
  ggplot(aes(x = In4_q90, y = nA, color = key))+
  geom_line()+
  geom_point()
 


# summarise(across(starts_with("Sepal"), list(mean = mean, sd = sd), .names = "{col}.{fn}"))


temp %>% 
  group_by(Sweep) %>% 
  filter(Time > peak_start & Time < peak_end) %>% 
  # filter(Time > end_start & Time < end_end) %>% 
  
  # ggplot(aes(x = In7, group = Sweep, color = Sweep))+geom_density()
  # summarise(across(In7, ~ ))
  

```




#### </ begin copy from 02ExtractEphysData.Rmd >


## IHTK
  1. plot to get user to say which to drop (if there is no file with this info) # done
  2. smooth # done
  3. get peak values # done
4. get sustained values
  5. subtract off leak # done
  6. report values and leak # done
```{r}
trace <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace <- janitor::clean_names(as.data.frame(trace), case = "big_camel")
trace <- trace %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace <- trace %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# gather(trace, channel, mV, c("In4", "In9")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.25, 0.3)
# 
# gather(trace, channel, mV, c("In7", "In12")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.27, 0.28)

trace <- trace %>% ungroup()

peaks <- trace %>% group_by(Sweep) %>% filter(RelativeTime > 0.27 & RelativeTime < 0.28) %>% summarise(max.val = max(In7)) %>%
  ungroup()


peaks$mV <- NA
for (i in seq(1, nrow(peaks), 1)){
  Sweep <- peaks[i, "Sweep"] %>% as.numeric()
  
  peaks[i, "mV"] <- trace[trace$Sweep == Sweep &
                            trace$RelativeTime > 0.27 &
                            trace$RelativeTime < 0.28 &
                            trace$In7 == as.numeric(peaks[peaks$Sweep == Sweep, "max.val"]), "In4"] %>% as.numeric() %>% mean(na.rm = T)
}



fm <- lm(max.val ~ mV, filter(peaks, mV < -41))

peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
peaks <- peaks %>% mutate(leak.sub = max.val - leak)


ggplot(peaks)+
  # geom_smooth(method = "lm")+
  lemon::geom_pointline(aes(x = mV, max.val))+
  lemon::geom_pointline(aes(x = mV, leak), color = "red")+
  lemon::geom_pointline(aes(x = mV, leak.sub), color = "blue")
  

# go through sweeps plotting each and asking if the user wants to keep each one. Then return a df with the ones to keep
checkSweeps <- function(
  trace = trace,
  v.ch = "In4",
i.ch = "In7",
t.ch = "RelativeTime"
){
  use.sweeps <- data.frame(Sweep = unique(trace$Sweep),
                         Use = rep(F, times = length(unique(trace$Sweep))))
trace <- as.data.frame(trace)
for (i in seq_along(unique(trace$Sweep))){
  # use.sweep <- F
  # par(mfrow = c(1, 2))
  par(mfrow = c(2, 1))
  # with({
  plot(trace[trace$Sweep == i, v.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l", 
       xlab="", ylab="",
       main = paste("Sweep",as.character(i)))
  plot(trace[trace$Sweep == i, i.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l",
       xlab="", ylab="")
  # })
  
  for (j in 1:3){
    print(paste0("Retain sweep ", as.character(i),"?"))
    print("T/F or E to Exit")
    
    user.input <- readline(prompt = ">")
    
    
    if (user.input == "E" | user.input == "e"){
      break()
      
    } else if (user.input == "T" | user.input == "t"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- T
      break()
      
    } else if (user.input == "F" | user.input == "f"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- F
      break()
      
    } else {
      print(paste("Response not recognized.", as.character(j), "attempts remain."))
    }
    
    
  }
  if (user.input == "E" | user.input == "e"){
    break()
  }
}
return(use.sweeps)
}



```


## IA
  1. plot to get user to say which to drop (if there is no file with this info)
  2. subract user supplied IHTK (don't smooth or filter, but drop any traces that aren't present for both)
  3. smooth
  4. get peak values
  5. get sustained values
 
```{r}
trace.htk <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace.htk <- janitor::clean_names(as.data.frame(trace.htk), case = "big_camel")
trace.htk <- trace.htk %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.htk <- trace.htk %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()



trace.a <-
readABF_as_matrix(
  path = paste0(path.base, file.a)
  )

trace.a <- janitor::clean_names(as.data.frame(trace.a), case = "big_camel")
trace.a <- trace.a %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.a <- trace.a %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# subtract traces
subtract_traces <- function(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
){
  # htk.data = trace.htk.data %>% head()
  # a.data = trace.a %>% head()
  # Time = "Time"
  # rel.time = "RelativeTime"
  # Sweep = "Sweep"
  # current.chs = c("In7", "In12")
  
  htk.data <- as.data.frame(htk.data)
  a.data <- as.data.frame(a.data)
  
  if (length(htk.data[[current.chs[1]]]) != length(a.data[[current.chs[1]]])){
    warning("Dataframe nrows are not equal!\nReturning nothing")
    return()
  } else {
    for (i in seq_along(current.chs)){
      a.data[[current.chs[i]]] <- a.data[[current.chs[i]]] - htk.data[[current.chs[i]]]
    }
    return(a.data)
  }
}



trace.a.ls <- subtract_traces(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
)


# Get max for a time window
find_local_max <- function(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
){
  # trace = trace.a.ls
  # window.start = 0.27
  # window.stop  = 0.28
  # Sweep = "Sweep"
  # RelativeTime = "RelativeTime"
  # i.ch = "In7"
  # v.ch = "In4"
  
  peaks <- trace %>% 
    group_by(Sweep) %>% 
    filter(RelativeTime > window.start & RelativeTime < window.stop) %>% 
    summarise(max.val = max(get(i.ch))) %>% 
    ungroup()
  
  peaks$mV <- NA
  for (i in seq(1, nrow(peaks), 1)){
    Sweep1 <- peaks[i, Sweep] %>% as.numeric()
    
    peaks[i, "mV"] <- trace[trace$Sweep == Sweep1 &
                              trace$RelativeTime > window.start &
                              trace$RelativeTime < window.stop &
                              trace[[i.ch]] == as.numeric(peaks[peaks$Sweep == Sweep1, "max.val"]), v.ch] %>% as.numeric() %>% mean(na.rm = T)
  }
  
  return(peaks)
}



max.a.ls <- 
find_local_max(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)



### comparisons
max.a <- 
find_local_max(
  trace = trace.a,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)


max.htk <- 
find_local_max(
  trace = trace.htk,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)

# Leak subtract max values
subtract_leak <- function(peaks = max.htk, # output from find_local_max
                          min.mV = -81,
                          max.mV = -39){
  # peaks = max.htk # output from find_local_max
  # min.mV = -81
  # max.mV = -39
  fm <- lm(max.val ~ mV, filter(peaks, mV <= max.mV & mV >= min.mV))
  
  peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
  peaks <- peaks %>% mutate(leak.sub = max.val - leak)
  return(peaks)
}


max.htk.ls <- subtract_leak(peaks = max.htk, # output from find_local_max
                            min.mV = -81,
                            max.mV = -39)


ggplot()+
  lemon::geom_pointline(data = max.htk, aes(x = mV, max.val), color = "#fc9272")+
  lemon::geom_pointline(data = max.htk.ls, aes(x = mV, leak.sub), color = "#de2d26")+
  lemon::geom_pointline(data = max.a, aes(x = mV, max.val), color = "#9ecae1")+
  lemon::geom_pointline(data = max.a.ls, aes(x = mV, max.val), color = "#3182bd")



```




# Older 

###HTK/A
#### </ begin copy from 02ExtractEphysData.Rmd >

---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# from TracesToTables.Rmd



```{r}
library(readABF)
library(here)
library(tidyverse)
```


```{r}
# Really just a wrapper for loadABF()
# readABF_as_matrix <- function(
#   path = "S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180117_inverted_wave/raw/180205_0061.abf",
#   channels = c("IN 4", "IN 9")){
# 
#   trace <- readABF::readABF(file = path)
# 
#   start.time <- trace$header$recTime[1]
#   end.time <- trace$header$recTime[2]
#   obs <- nrow(trace$data[[1]])
# 
#   temp <- trace$data[[1]][, (trace$channelNames %in% channels)]
#   temp <- as.matrix(temp)
# 
#   colnames(temp) <- trace$channelNames[trace$channelNames %in% channels]
#   temp <- cbind(temp, Time = seq(from = start.time,
#                                  to = end.time,
#                                  length.out = obs))
# 
#   return(temp)
# }

```



```{r}
# Set here not working as expected. Does it need to go in here?
# set_here(path = "/Volumes/schulzlab/Data_Daniel/ActiveProjects/mRNA24hLCAcquisition", verbose = TRUE)
# 
# #rin path
# use.path <- here(#"/Volumes/schulzlab/Data_Daniel/ActiveProjects/mRNA24hLCAcquisition/"
#   "1h_TEA",
#   "190308_0028.abf")
# 
# # list.files("/Volumes/schulzlab/Data_Daniel/ActiveProjects/mRNA24hLCAcquisition/1h_TEA")
#    

# path.base <- "/Volumes/schulzlab/Data_Daniel/ActiveProjects/mRNA24hLCAcquisition/1h_TEA/"
path.base <- "S:/Data_Daniel/ActiveProjects/mRNA24hLCAcquisition/1h_TEA/"

file.free <- "190306_0047.abf"

# file.rin <- "190306_0052.abf"

file.tecc.gj <- "190306_0052.abf"

file.epsp <- "190306_0053.abf"
file.fi <- "190306_0056.abf"

file.tevc.gj <- "190306_0057.abf"
file.htk <- "190306_0060.abf"
file.a <- "190306_0061.abf"
file.htk.c <- "190306_0062.abf"
file.a.c <- "190306_0063.abf"


# trace <- readABF(paste0(path.base, file.htk))
# 
# $ channelNames         : chr [1:4] "IN 4" "IN 7" "IN 9" "IN 12"
#  $ data                 :List of 11
# 
# plot(trace$data[[1]][, 1])
# plot(trace$data[[2]][, 1])

readABF_as_matrix <- function(
  path = "S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180117_inverted_wave/raw/180205_0061.abf"#,
  # channels = c("IN 4", "IN 9")
  ){

  # path = paste0(path.base, file.htk)
  # channels = c("IN 4", "IN 9")
  
  trace <- readABF::readABF(file = path)

  start.time <- trace$header$recTime[1]
  end.time <- trace$header$recTime[2]
  
  for (i in seq_along(trace$data)){
    # print(i)
  
  
  # obs <- nrow(trace$data[[i]])

  temp <- trace$data[[i]]#[, (trace$channelNames %in% channels)]
  temp <- as.matrix(temp)

  colnames(temp) <- trace$channelNames#[trace$channelNames %in% channels]
  temp <- cbind(temp, Sweep = rep(i, times = nrow(temp)))
  # temp <- cbind(temp, Time = seq(from = start.time,
  #                                to = end.time,
  #                                length.out = obs))
  if (i == 1){
    output <- temp
  } else {
    output <- rbind(output, temp)
  }
  }
  
  # Moved here to account for multi sweep protocols
    output <- cbind(output, Time = seq(from = start.time,
                                 to = end.time,
                                 length.out = nrow(output)))
  
  return(output)
}
```

# Current clamp protocols

## Rin

## Fi
Needs to 
  1. get voltage traces
  2. get AUC


```{r}
```



## EPSP mimic
Needs to 
  1. get voltage traces
  2. correlate between them
  3. correlate burst only portion?

# Voltage Clamp Protocols

## TEVC GJ
Needs to 
  1. get step values
  2. calculate ig via spray and bennet
  3. save control potential as well
```{r}
trace <-
readABF_as_matrix(
  path = paste0(path.base, file.tevc.gj)
  )

trace <- janitor::clean_names(as.data.frame(trace), case = "big_camel")
trace <- trace %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time))


ggplot(trace, aes(x = RelativeTime, y = In4, group = Sweep))+
  geom_line()+
  ylim(-100, 100)

plot(`In7` ~ RelativeTime, type = "l", data = trace)

```

```{r}
trace = trace
v1 = "In4"
i1 = "In7"
v2 = "In9"
i2 = "In12"
window.start = 0.4
window.stop = 0.5
Sweep = "Sweep"

#Spray, Harris, and Bennett 1979 states:
#"This transjunctional current (Ij) injected into the second cell gives a direct measure of junctional conductance when dividded by the the magnitude of the step change in transjunctional voltage"

 # trace = trace.htk,
 # 
 #  RelativeTime = "RelativeTime",
 #  i.ch = "In7",
 #  v.ch = "In4"

```




```{r infer mv steps 2, }

df.tevc_gj <- df.tevc_gj[!is.na(df.tevc_gj$IN4_mean), ]
df.tevc_gj <- df.tevc_gj[!is.na(df.tevc_gj$IN9_mean), ]

df.tevc_gj$inj_in_IN4 <- abs(df.tevc_gj$IN4_mean) > abs(df.tevc_gj$IN9_mean) #So we can appropriately apply the formula

df.tevc_gj$diff_in_means <- abs(df.tevc_gj$IN4_mean) - abs(df.tevc_gj$IN9_mean) #so we can drop the ones where both are held at 60mV
df.tevc_gj <- df.tevc_gj[abs(df.tevc_gj$diff_in_means) > 6,] #drop the 0mv step and the +/-5mV steps

#Apply Spray, Harris, and Bennett's calculation
df.tevc_gj$gj <- 0
df.tevc_gj[df.tevc_gj$inj_in_IN4 == FALSE, "gj"] <- df.tevc_gj[df.tevc_gj$inj_in_IN4 == FALSE, "IN7_mean"] / df.tevc_gj[df.tevc_gj$inj_in_IN4 == FALSE, "IN9_mean"]
df.tevc_gj[df.tevc_gj$inj_in_IN4 == TRUE, "gj"] <- df.tevc_gj[df.tevc_gj$inj_in_IN4 == TRUE, "IN12_mean"] / df.tevc_gj[df.tevc_gj$inj_in_IN4 == TRUE, "IN4_mean"]


#Add this column for later
df.tevc_gj[df.tevc_gj$inj_in_IN4 == TRUE, "Inj_Cell"] <- df.tevc_gj[df.tevc_gj$inj_in_IN4 == TRUE, "IN4"]
df.tevc_gj[df.tevc_gj$inj_in_IN4 == FALSE, "Inj_Cell"] <- df.tevc_gj[df.tevc_gj$inj_in_IN4 == FALSE, "IN9"]
```

```{r add directionality}
df.tevc_gj[df.tevc_gj$Inj_Cell == "LC4", "Direction"] <- "LC4 -> LC5"
df.tevc_gj[df.tevc_gj$Inj_Cell == "LC5", "Direction"] <- "LC5 -> LC4"

df.tevc_gj[, "interact"] <- interaction(df.tevc_gj$Experiment, df.tevc_gj$Direction)
```


## IHTK
  1. plot to get user to say which to drop (if there is no file with this info) # done
  2. smooth # done
  3. get peak values # done
4. get sustained values
  5. subtract off leak # done
  6. report values and leak # done
```{r}
trace <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace <- janitor::clean_names(as.data.frame(trace), case = "big_camel")
trace <- trace %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace <- trace %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# gather(trace, channel, mV, c("In4", "In9")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.25, 0.3)
# 
# gather(trace, channel, mV, c("In7", "In12")) %>% ggplot(aes(RelativeTime, mV, color = channel, group = Sweep))+geom_line()+xlim(0.27, 0.28)

trace <- trace %>% ungroup()

peaks <- trace %>% group_by(Sweep) %>% filter(RelativeTime > 0.27 & RelativeTime < 0.28) %>% summarise(max.val = max(In7)) %>%
  ungroup()


peaks$mV <- NA
for (i in seq(1, nrow(peaks), 1)){
  Sweep <- peaks[i, "Sweep"] %>% as.numeric()
  
  peaks[i, "mV"] <- trace[trace$Sweep == Sweep &
                            trace$RelativeTime > 0.27 &
                            trace$RelativeTime < 0.28 &
                            trace$In7 == as.numeric(peaks[peaks$Sweep == Sweep, "max.val"]), "In4"] %>% as.numeric() %>% mean(na.rm = T)
}



fm <- lm(max.val ~ mV, filter(peaks, mV < -41))

peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
peaks <- peaks %>% mutate(leak.sub = max.val - leak)


ggplot(peaks)+
  # geom_smooth(method = "lm")+
  lemon::geom_pointline(aes(x = mV, max.val))+
  lemon::geom_pointline(aes(x = mV, leak), color = "red")+
  lemon::geom_pointline(aes(x = mV, leak.sub), color = "blue")
  

# go through sweeps plotting each and asking if the user wants to keep each one. Then return a df with the ones to keep
checkSweeps <- function(
  trace = trace,
  v.ch = "In4",
i.ch = "In7",
t.ch = "RelativeTime"
){
  use.sweeps <- data.frame(Sweep = unique(trace$Sweep),
                         Use = rep(F, times = length(unique(trace$Sweep))))
trace <- as.data.frame(trace)
for (i in seq_along(unique(trace$Sweep))){
  # use.sweep <- F
  # par(mfrow = c(1, 2))
  par(mfrow = c(2, 1))
  # with({
  plot(trace[trace$Sweep == i, v.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l", 
       xlab="", ylab="",
       main = paste("Sweep",as.character(i)))
  plot(trace[trace$Sweep == i, i.ch] ~ trace[trace$Sweep == i, t.ch], 
       type = "l",
       xlab="", ylab="")
  # })
  
  for (j in 1:3){
    print(paste0("Retain sweep ", as.character(i),"?"))
    print("T/F or E to Exit")
    
    user.input <- readline(prompt = ">")
    
    
    if (user.input == "E" | user.input == "e"){
      break()
      
    } else if (user.input == "T" | user.input == "t"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- T
      break()
      
    } else if (user.input == "F" | user.input == "f"){
      use.sweeps[use.sweeps$Sweep == i, "Use"] <- F
      break()
      
    } else {
      print(paste("Response not recognized.", as.character(j), "attempts remain."))
    }
    
    
  }
  if (user.input == "E" | user.input == "e"){
    break()
  }
}
return(use.sweeps)
}



```


## IA
  1. plot to get user to say which to drop (if there is no file with this info)
  2. subract user supplied IHTK (don't smooth or filter, but drop any traces that aren't present for both)
  3. smooth
  4. get peak values
  5. get sustained values
 
```{r}
trace.htk <-
readABF_as_matrix(
  path = paste0(path.base, file.htk)
  )

trace.htk <- janitor::clean_names(as.data.frame(trace.htk), case = "big_camel")
trace.htk <- trace.htk %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.htk <- trace.htk %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()



trace.a <-
readABF_as_matrix(
  path = paste0(path.base, file.a)
  )

trace.a <- janitor::clean_names(as.data.frame(trace.a), case = "big_camel")
trace.a <- trace.a %>% group_by(Sweep) %>% mutate(RelativeTime = Time - min(Time)) %>%
  ungroup()
trace.a <- trace.a %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = 7, fill = NA)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = 7, fill = NA)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = 7, fill = NA)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = 7, fill = NA)) %>%
  ungroup()

# subtract traces
subtract_traces <- function(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
){
  # htk.data = trace.htk.data %>% head()
  # a.data = trace.a %>% head()
  # Time = "Time"
  # rel.time = "RelativeTime"
  # Sweep = "Sweep"
  # current.chs = c("In7", "In12")
  
  htk.data <- as.data.frame(htk.data)
  a.data <- as.data.frame(a.data)
  
  if (length(htk.data[[current.chs[1]]]) != length(a.data[[current.chs[1]]])){
    warning("Dataframe nrows are not equal!\nReturning nothing")
    return()
  } else {
    for (i in seq_along(current.chs)){
      a.data[[current.chs[i]]] <- a.data[[current.chs[i]]] - htk.data[[current.chs[i]]]
    }
    return(a.data)
  }
}



trace.a.ls <- subtract_traces(
  htk.data = trace.htk,
  a.data = trace.a,
  current.chs = c("In7", "In12")
)


# Get max for a time window
find_local_max <- function(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
){
  # trace = trace.a.ls
  # window.start = 0.27
  # window.stop  = 0.28
  # Sweep = "Sweep"
  # RelativeTime = "RelativeTime"
  # i.ch = "In7"
  # v.ch = "In4"
  
  peaks <- trace %>% 
    group_by(Sweep) %>% 
    filter(RelativeTime > window.start & RelativeTime < window.stop) %>% 
    summarise(max.val = max(get(i.ch))) %>% 
    ungroup()
  
  peaks$mV <- NA
  for (i in seq(1, nrow(peaks), 1)){
    Sweep1 <- peaks[i, Sweep] %>% as.numeric()
    
    peaks[i, "mV"] <- trace[trace$Sweep == Sweep1 &
                              trace$RelativeTime > window.start &
                              trace$RelativeTime < window.stop &
                              trace[[i.ch]] == as.numeric(peaks[peaks$Sweep == Sweep1, "max.val"]), v.ch] %>% as.numeric() %>% mean(na.rm = T)
  }
  
  return(peaks)
}



max.a.ls <- 
find_local_max(
  trace = trace.a.ls,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)



### comparisons
max.a <- 
find_local_max(
  trace = trace.a,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)


max.htk <- 
find_local_max(
  trace = trace.htk,
  window.start = 0.27,
  window.stop  = 0.28,
  Sweep = "Sweep",
  RelativeTime = "RelativeTime",
  i.ch = "In7",
  v.ch = "In4"
)

# Leak subtract max values
subtract_leak <- function(peaks = max.htk, # output from find_local_max
                          min.mV = -81,
                          max.mV = -39){
  # peaks = max.htk # output from find_local_max
  # min.mV = -81
  # max.mV = -39
  fm <- lm(max.val ~ mV, filter(peaks, mV <= max.mV & mV >= min.mV))
  
  peaks <- peaks %>% mutate(leak = predict(object = fm, newdata = peaks))
  peaks <- peaks %>% mutate(leak.sub = max.val - leak)
  return(peaks)
}


max.htk.ls <- subtract_leak(peaks = max.htk, # output from find_local_max
                            min.mV = -81,
                            max.mV = -39)


ggplot()+
  lemon::geom_pointline(data = max.htk, aes(x = mV, max.val), color = "#fc9272")+
  lemon::geom_pointline(data = max.htk.ls, aes(x = mV, leak.sub), color = "#de2d26")+
  lemon::geom_pointline(data = max.a, aes(x = mV, max.val), color = "#9ecae1")+
  lemon::geom_pointline(data = max.a.ls, aes(x = mV, max.val), color = "#3182bd")



```


# Assess Data
```{r}
metadata <- read.csv("./inst/extdata/MetadataEphys.csv")

metadata %>% 
  gather(Channel, Cell, c("In4", "In9")) %>% 
  select(c("Experiment", "Condition", "Cell")) %>% 
  group_by(Condition) %>% 
  unique() %>% 
  tally() %>% 
  ungroup()
```



```{r}
# write file name from spreadsheet
mk_filename <- function(
  metadata.file = metadata,
  use.row = 1){
  filename <- paste0(
    as.character(
      metadata.file[use.row, "Experiment"]
    ),
    "_",
    paste0(
      rep("0", (4-length(metadata.file[use.row, "Recording"]))), collapse = ""),
    as.character(
      metadata.file[1, "Recording"]
    ),
    ".abf"
  )
  return(filename)
}


# select a prep and check that the file type isn't nonsensical
prep_abf <- function(
  file.name = "190306_0063.abf", #mk_filename()
  file.type = "ac" #metadata[row.num, "Type"] 
){
  M <- readABF_as_matrix(here("inst", "extdata", "all_traces", file.name)) %>% 
    # as.data.table() %>% 
    as.data.frame() %>% 
    janitor::clean_names(., case = "big_camel")
  
  # This is here to get rid of an unknown/uninitialized col warning
  M <- M[, names(M) ]
  
  # if metadata says its...
  if (file.type %in% c("gf")){
    # [1] "IN 4"  "IN 9"  "IN 14" "Sweep" "Time" # gap free
    #TODO
  } else if (file.type %in% c("tecc.gj")){
    # [1] "IN 4"  "IN 6"  "IN 7"  "IN 9"  "IN 11" "IN 12" "Sweep" "Time" # tecc.gj
    #TODO
  } else if (file.type %in% c("epsp")){
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "IN 14" "Sweep" "Time" # epsp
    #TODO
  } else if (file.type %in% c("fi")){
    # [1] "IN 4"  "IN 6"  "IN 7"  "IN 9"  "IN 11" "IN 12" "IN 14" "Sweep" "Time" # fi
    #TODO
  } else if (file.type %in% c("htk", "a", "htkc", "ac")){
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "Sweep" "Time" # tevc.gj
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "Sweep" "Time" # htk
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "Sweep" "Time" # a
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "Sweep" "Time" # htkc
    # [1] "IN 4"  "IN 7"  "IN 9"  "IN 12" "Sweep" "Time" # ac
    if (mean(names(M) %in% c("In4", "In7", "In9", "In12", "Sweep", "Time")) != 1){
      warning(
        paste(as.character(file.name), 
              as.character(file.type), 
              "NAMES EXPECTED:", "In4", "In7", "In9", "In12", "Sweep", "Time", 
              "NAMES FOUND:", paste(names(M), collapse = " ")
        )
      )
    } 
  } else {
    warning(paste("file type", as.character(file.type), "not recognized!"))
  }
  return(M)
}


mk_rel_time <- function(df = Trace){
  df <- df %>% 
    group_by(Sweep) %>% 
    mutate(RelativeTime = Time - min(Time)) %>%
    ungroup()
  return(as.data.frame(df))
}

rollmean_tevc <- function(df = Trace,
                          use.k = 7,
                          use.fill = NA){
  df <- df %>% group_by(Sweep) %>% 
  mutate(In4  = zoo::rollmean(In4,  k = use.k, fill = use.fill)) %>% 
  mutate(In7  = zoo::rollmean(In7,  k = use.k, fill = use.fill)) %>% 
  mutate(In9  = zoo::rollmean(In9,  k = use.k, fill = use.fill)) %>% 
  mutate(In12 = zoo::rollmean(In12, k = use.k, fill = use.fill)) %>%
  ungroup()
  return(as.data.frame(df))
}

process_htk <- function(use.nrow = 5,
                        use.metadata = htks,
                        use.window.start = 0.27,
                        use.window.stop = 0.28,
                        leak.min.mV = -81,
                        leak.max.mV = -39){
  
  M <- mk_filename(
    metadata.file = use.metadata,
    use.row = use.nrow
  ) %>% prep_abf(
    file.name = .,
    file.type = use.metadata[use.nrow, "Type"]
  ) %>% 
    mk_rel_time(df = .) 
    rollmean_tevc(
    df = .,
    use.k = 7,
    use.fill = NA
  )
  
  # is there data in the In4/In7 pair?
  if (use.metadata %>% slice(use.nrow) %>% select(In4) == ""){
    # do nothing
    In4.data <- data.frame()
    
  } else {
    In4.data <- 
      find_local_max(
        trace = M,
        window.start = use.window.start,
        window.stop  = use.window.stop,
        Sweep = "Sweep",
        RelativeTime = "RelativeTime",
        i.ch = "In7",
        v.ch = "In4"
      ) %>% 
      subtract_leak(peaks = ., # output from find_local_max
                    min.mV = leak.min.mV,
                    max.mV = leak.max.mV) %>% 
      mutate(Cell = use.metadata %>% slice(use.nrow) %>% select(In4) %>% as.character())
    
  }
  # is there data in the In9/In12 pair?
  if (use.metadata %>% slice(use.nrow) %>% select(In9) == ""){
    # do nothing
    In9.data <- data.frame()
    
  } else {
    In9.data <- 
      find_local_max(
        trace = M,
        window.start = use.window.start,
        window.stop  = use.window.stop,
        Sweep = "Sweep",
        RelativeTime = "RelativeTime",
        i.ch = "In12",
        v.ch = "In9"
      ) %>% 
      subtract_leak(peaks = ., # output from find_local_max
                    min.mV = leak.min.mV,
                    max.mV = leak.max.mV) %>% 
      mutate(Cell = use.metadata %>% slice(use.nrow) %>% select(In9) %>% as.character())
    
  }
  
  # Since we set these as an empty data.frame if there is no cell we can rbind without fear of a problem.
  return(rbind(In4.data, In9.data))
}
```


```{r}
#find all htks
htks <- metadata %>% 
  filter((Pharm == "none" | Pharm == "tea") & Type == "htk") %>% 
  select(Experiment, Recording, Type, Condition, In4, In9) %>% 
  arrange(Condition)

# row 5 is not htk. has only
# In4       In9         In14 Sweep     Time

for (i in 1:NROW(htks)){
  plt <- process_htk(use.nrow = 8,
                     use.metadata = htks,
                     use.window.start = 0.27,
                     use.window.stop = 0.28,
                     leak.min.mV = -81,
                     leak.max.mV = -39) %>% 
    gather(type, i, c("max.val", "leak", "leak.sub")) %>% 
    ggplot(aes(x = mV, y = i, group = type, color = type))+
    geom_line()+
    geom_point()+
    facet_grid(.~Cell)+
    theme_dark()+
    labs(title = as.character(i)) 
  plot(plt)
}




max.htk.ls <- subtract_leak(peaks = max.htk, # output from find_local_max
                            min.mV = -81,
                            max.mV = -39)
```

